---
title: "ASCOT Anticoagulation Clinical Study Report"
date: '2022-06-30'
author:
  - name: James Totterdell
    affiliation: University of Sydney
  - name: Rob Mahar
    affiliation: University of Melbourne
format:
  pdf:
    documentclass: scrreprt
    toc: true
    number-sections: true
    colorlinks: true
    lof: true
    lot: true
    linestretch: "1.2"
    mainfont: TeX Gyre Pagella
    mathfont: TeX Gyre Pagella Math
    monofont: TeX Gyre Cursor
    sansfont: TeX Gyre Heros
    include-in-header:
      - packages.tex
execute: 
  echo: false
---

# Synopsis

# Introduction

## Purpose

The trial steering committee (TSC) closed randomisation to the anticoagulation domain on xx xxx 2022. The blinded statistical analysis workin group prepared a statistical analysis plan (SAP) for reporting the results of the anticoagulation domain. The unblinded team of statisticians undertook these analysis using the relevant records as extracted from the database on 2022-06-06.

This report summarises the data and results for the anticoagulation domain. The report restricts these summaries and analyses to the interventions available in the anticoagulation domain and does not report on the interventions in the antiviral domain.

## Trial Status


# Results

## Study Population

### Summary

At the time of database lock for the anticoagulation domain, 1,599 participants had been enrolled onto the study platform and 1,574 participants had been randomised to the anticoagulation domain. The first participant was randomised on 2021-02-08 and the last participant enrolled into the anticoagulation domain was randomised on 2022-03-29.

### Disposition

Of the 1,574 participants randomised to the anticoagulation domain, 18 withdrew consent for follow-up leaving 1,556 participants continuing to study day 28. The analyses and summaries included in this report exclude data on participants who withdrew consent for follow-up.

Platform and domain specific flow diagrams are included in @fig-platform-flow and @fig-anticoagulation-flow respectively.

![Platform flowchart.](platform_flowchart.tex){#fig-platform-flow}

![Anticoagulation domain flowchart.](domain_anticoagulation_flowchart.tex){#fig-anticoagulation-flow}

@fig-enrolments presents overall platform enrolments by calendar time with timing of intervention availabilities and interim analyses. Enrolments by country are presented in @fig-enrolments-country. Due to the changes to the trial which occurred independently of the within trial results, the initial allocation ratios were not changed during recruitment to the anticoagulation domain. Therefore, the only trial adaptations which occurred were the cessation of the standard dose plus aspirin intervention in the anticoagulation domain, the opening of the antiviral domain, and the introduction of the therapeutic dose intervention into the anticoagulation domain. Despite this, the timing of interim analyses are indicated on the Figures.

```{r}
#| label: fig-enrolments
#| fig-cap: |
#|   Overall enrolment to the anti-coagulation domain and intervention availability.
#|   Vertical dashed lines indicate timing of interim analyses.
knitr::include_graphics(
  "../outputs/figures/baseline/enrolment-overall.pdf"
)
```

```{r}
#| label: fig-enrolments-country
#| fig-cap: |
#|   Enrolment to platform and intervention availability by country.
#|   Vertical dashed lines indicate timing of interim analyses.
knitr::include_graphics(
  "../outputs/figures/baseline/enrolment-country.pdf"
)
```

```{r}
#| label: fig-enrolments-india-sites
#| fig-cap: |
#|   Enrolment to sites in India. 
#|   Vertical dashed lines indicate timing of interim analyses.
knitr::include_graphics(
  "../outputs/figures/baseline/enrolment-india-sites.pdf"
)
```

```{r}
#| label: fig-enrolments-australia-sites
#| fig-cap: |
#|   Enrolment to sites in Australia. 
#|   Vertical dashed lines indicate timing of interim analyses.
knitr::include_graphics(
  "../outputs/figures/baseline/enrolment-australia-sites.pdf"
)
```

```{r}
#| label: fig-enrolments-nepal-nz-sites
#| fig-cap: |
#|   Enrolment to sites in Nepal and New Zealand 
#|   Vertical dashed lines indicate timing of interim analyses.
knitr::include_graphics(
  "../outputs/figures/baseline/enrolment-nepalnz-sites.pdf"
)
```

\clearpage

### Intervention Allocations

\clearpage

### Deviations

{{< pagebreak >}}

### Analysis Sets

The primary analysis population includes all participants who were randomised to the anticoagulation domain. For the intention-to-treat (ITT) analysis, all participants randomised to the anticoagulation domain were analysed according to their aside regimen irrespective of deviations or non-adherence.

Secondary analyses expand the analysis set to include all participants randomised to the platform including those who were not randomised to the anticoagulation domain for the purpose of additional covariate information.

Per-protocol (PP) analyses restrict both of analysis sets to only those participants who sufficiently adhered to the protocol as determined by blinded review. Participants who were not PP had their outcomes set to missing.

### Baseline Characteristics

#### Demographics

Baseline demographics stratified by anticoagulation interventions are reported in @tbl-baseline-demographics
```{r}
#| label: tbl-baseline-demographics
#| tbl-cap: |
#|   Baseline demographics for participants randomised to the anticoagulation domain.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "baseline", "demographics.tex"))
writeLines(tab[-which(grepl("caption", tab))])
```

The age distribution of participants are presented in @fig-age-overall.
```{r}
#| label: fig-age-overall
#| fig-cap: |
#|   Distribution of age amongst participants randomised to the anticoagulation domain.
knitr::include_graphics(
  "../outputs/figures/baseline/age-overall.pdf"
)
```

#### Co-morbidities

Baseline co-morbidities stratified by anticoagulation interventions are reported in @tbl-baseline-comorbidities.
```{r}
#| label: tbl-baseline-comorbidities
#| tbl-cap: |
#|   Baseline comorbidities for participants randomised to the anticoagulation domain.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "baseline", "comorbidities.tex"))
writeLines(tab[-which(grepl("caption", tab))])
```

#### Prognostics

Baseline prognostics stratified by anticoagulation interventions are reported in @tbl-baseline-prognostics.
```{r}
#| label: tbl-baseline-prognostics
#| tbl-cap: |
#|   Baseline prognostics for participants randomised to the anticoagulation domain.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "baseline", "prognostics.tex"))
writeLines(tab[-which(grepl("caption", tab))])
```

The relative timing (in days) of hospitalisation, symptom onset, randomisation, and first positive test are presented in @fig-days-to-events-overall.
```{r}
#| label: fig-days-to-events-overall
#| fig-cap: |
#|   Days between events for hospitalisation, randomisation,
#|   symptom onset, and first positive test.
knitr::include_graphics(
  "../outputs/figures/baseline/days-between-events-overall.pdf"
)
```

\clearpage

### Drugs Received During Hospital Stay

There were 19 participants without a discharge record (due to withdrawal of consent for follow-up). For the continuing participants, the other medications received during their hospital stay are reported in @tbl-discharge-drugs.

```{r}
#| label: tbl-discharge-drugs
#| tbl-cap: |
#|   Drugs received during hospital stay for participants randomised to 
#|   the anti-coagulation domain.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "baseline", "drugs.tex"))
writeLines(tab[-which(grepl("caption", tab))])
```


### Adherence

\clearpage

## Analyses - General

Bayesian models were computed using Stan via `cmdstanr` (0.5.2 and cmdstan version 2.29.2) in R (4.2.0). For each model, 8 chains were used with a burn in of 500 and sampling of 2500 iterations per chain. Convergence diagnostics were assessed for each model. If an issue was identified (e.g. divergent transitions) then the default sampling parameters may have been adjusted (e.g. increasing target acceptance rate or increasing maximum tree depth). If any convergence issues remained they will be reported along with the model results. If the model was amended in any way to satisfy convergence criteria (e.g. aggregation of groups) then this will be reported in the relevant section. Sampling was run using a different (randomly selected) random seed for each model, and these were recorded for replication.

## Primary Outcome

The primary outcome is a composite comprised of:

- day 28 mortality
- vasopressor/inotropic support within first 28 days
- new intensive respiratory support within first 28 days.

The proportion of participants who met the primary outcome, and rates of missingness, are reported in @tbl-primary-composite-summary.

```{r}
#| label: tbl-primary-composite-summary
#| tbl-cap: |
#|   Summary of primary composite outcome by treatment group.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "anticoagulation-summary.tex"))
writeLines(tab)
```

A breakdown of the composite, including missingness by component is reported in @tbl-primary-composite-breakdown. Missingness is predominantly due to unknown patient status at study day 28. Amongst participants where the primary outcome was observed (1,526), 103 (7%) met the primary outcome criteria, most commonly due to ventilation and/or death (@tbl-primary-composite-combinations).

```{r}
#| label: tbl-primary-composite-breakdown
#| tbl-cap: |
#|   Breakdown of primary composite outcome by treatment group.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "composite-breakdown.tex"))
writeLines(tab)
```

### Primary Analysis

The primary model was a logistic regression model adjusting for anticoagulation treatment, antiviral treatment, age ($\geq 60$), and country, with random effects for site (nested within country) and epoch (calendar time 4 week intervals). The two most recent epochs were combined due to small numbers, and the two earliest epochs were combined for the same reason.

#### Full Model ACS-ITT set

The primary analysis was based on the ACS-ITT set using the full model as specified in the statistical appendix to the core protocol.

```{r}
#| label: tbl-primary-model-acs-itt-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for primary model fit to the ACS-ITT set.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "primary-model-acs-itt-summary-table.tex"))
writeLines(tab)
```

#### Sensitivity

##### FAS-ITT

The primary model was fit to the expanded FAS-ITT set. The model treatment effects were similar to those obtained under the ACS-ITT set.

```{r}
#| label: tbl-primary-model-fas-itt-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for primary model fit to the FAS-ITT set.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "primary-model-fas-itt-summary-table.tex"))
writeLines(tab)
```


\clearpage

## Secondary Outcomes

### Time to clinical recovery

### All-cause mortality

All-cause mortality to day 28 was modelled using the same method as for the primary outcome.

### WHO outcome scale

### Days free of hospitalisation

\clearpage

## Domain Specific Outcomes

## Safety

# Appendices {.unnumbered}
