---
title: "ASCOT Anticoagulation Clinical Study Report"
date: '2022-06-15'
author:
  - name: James Totterdell
    affiliation: University of Sydney
  - name: Rob Mahar
    affiliation: University of Melbourne
format:
  pdf:
    documentclass: scrreprt
    toc: true
    toc-depth: 4
    number-sections: true
    colorlinks: true
    lof: true
    lot: true
    linestretch: "1.2"
    mainfont: TeX Gyre Pagella
    mathfont: TeX Gyre Pagella Math
    monofont: TeX Gyre Cursor
    sansfont: TeX Gyre Heros
    include-in-header:
      - packages.tex
execute: 
  echo: false
---

# Synopsis

# Introduction

## Purpose

The trial steering committee (TSC) closed randomisation to the anticoagulation domain on 8 April 2022. The blinded statistical analysis working group prepared a statistical analysis plan (SAP) for reporting the results of the anticoagulation domain. The unblinded team of statisticians undertook these analysis using the relevant records as extracted from the database on 2022-06-06.

This report summarises the data and results for the anticoagulation domain. The report restricts these summaries and analyses to the interventions available in the anticoagulation domain and does not report on the interventions in the antiviral domain.

## Primary Model

The primary model was a logistic regression model where a value of 1 indicates a patient met the primary outcome, and a value of 0 indicates they did not. The model included terms for the anticoagulation intervention received, the antiviral intervention received, intervention specific eligibilities, age at trial entry, region of enrolment, site of enrolment, and epoch of enrolment.

# Results

## Study Population

### Summary

At the time of database lock for the anticoagulation domain, 1,599 participants had been enrolled onto the study platform and 1,574 participants had been randomised to the anticoagulation domain. The first participant was randomised on 2021-02-08 and the last participant enrolled into the anticoagulation domain was randomised on 2022-03-29.

### Disposition

Of the 1,574 participants randomised to the anticoagulation domain, 18 withdrew consent for follow-up leaving 1,556 participants continuing to study day 28. The analyses and summaries included in this report exclude data on participants who withdrew consent for follow-up.

Platform and domain specific flow diagrams are included in @fig-platform-flow and @fig-anticoagulation-flow respectively.

![Platform flowchart.](platform_flowchart.tex){#fig-platform-flow}

![Anticoagulation domain flowchart.](domain_anticoagulation_flowchart.tex){#fig-anticoagulation-flow}

@fig-enrolments presents overall platform enrolments by calendar time with timing of intervention availabilities and interim analyses. Enrolments by country are presented in @fig-enrolments-country. Due to the changes to the trial which occurred independently of the within trial results, the initial allocation ratios were not changed during recruitment to the anticoagulation domain. Therefore, the only trial adaptations which occurred were the cessation of the standard dose plus aspirin intervention in the anticoagulation domain, the opening of the antiviral domain, and the introduction of the therapeutic dose intervention into the anticoagulation domain. Despite this, the timing of interim analyses are indicated on the Figures.

```{r}
#| label: fig-enrolments
#| fig-cap: |
#|   Overall enrolment to the anti-coagulation domain and intervention availability.
#|   Vertical dashed lines indicate timing of interim analyses.
knitr::include_graphics(
  "../outputs/figures/baseline/enrolment-overall.pdf"
)
```

```{r}
#| label: fig-enrolments-country
#| fig-cap: |
#|   Enrolment to platform and intervention availability by country.
#|   Vertical dashed lines indicate timing of interim analyses.
knitr::include_graphics(
  "../outputs/figures/baseline/enrolment-country.pdf"
)
```

```{r}
#| label: fig-enrolments-india-sites
#| fig-cap: |
#|   Enrolment to sites in India. 
#|   Vertical dashed lines indicate timing of interim analyses.
knitr::include_graphics(
  "../outputs/figures/baseline/enrolment-india-sites.pdf"
)
```

```{r}
#| label: fig-enrolments-australia-sites
#| fig-cap: |
#|   Enrolment to sites in Australia. 
#|   Vertical dashed lines indicate timing of interim analyses.
knitr::include_graphics(
  "../outputs/figures/baseline/enrolment-australia-sites.pdf"
)
```

```{r}
#| label: fig-enrolments-nepal-nz-sites
#| fig-cap: |
#|   Enrolment to sites in Nepal and New Zealand 
#|   Vertical dashed lines indicate timing of interim analyses.
knitr::include_graphics(
  "../outputs/figures/baseline/enrolment-nepalnz-sites.pdf"
)
```

\clearpage

### Intervention Allocations

Due to the trial progression, response adaptive randomisation (RAR) was never activated in the anticoagulation domain. Therefore, target allocations to the interventions were uniform across all available interventions from trial start to trial closure. However, the available interventions did change over time. The following figures summarise treatment allocations over time and by country.

\clearpage

### Deviations

Protocol deviations...

\clearpage

### Analysis Sets {#sec-analysis-sets}

The primary analysis population includes all participants who were randomised to the anticoagulation domain. For the intention-to-treat (ITT) analyses, all participants randomised to the anticoagulation domain were analysed according to their aside regimen irrespective of deviations or non-adherence. This set is referred to as the anticoagulation ITT set (ACS-ITT).

Secondary analyses expand the analysis set to include all participants randomised to the platform including those who were not randomised to the anticoagulation domain for the purpose of additional covariate information. This is referred to as the full analysis set ITT (FAS-ITT)

Per-protocol (PP) analyses restrict both of the analysis sets to only those participants who sufficiently adhered to the protocol as determined by blinded review. Participants who were not PP had their outcomes set to missing, (ACS-PP and FAS-PP).

Additional analysis sets are defined for the purpose of comparing the interventions restricted to the timing of concurrent randomisation. For this purpose, the following additional analysis sets are specified:

-   ACS-ITT-intermediate: ACS-ITT set restricted to only patients randomised into either standard dose or intermediate dose intervention.
-   ACS-ITT-aspirin: ACS-ITT set restricted to patients randomised between 2021-02-08 (domain start) and 2021-09-10 (closure of aspirin arm) who were eligible for the standard dose plus aspirin intervention
-   ACS-ITT-therapeutic: ACS-ITT set restricted to patients randomised under protocol version 5.0 (which introduced the therapeutic dose arm), noting that each site may have activated version 5.0 of the protocol at different times (or may never have activated it).

| Name                 | Definition                                                                                                                                                                                                     |
|-----------------------|-----------------------------------------------------------|
| FAS-ITT              | All participants who were randomised to at least one study domain. Participants will be analysed as randomised, irrespective of withdrawal from treatment, treatment compliance, or other protocol deviations. |
| ACS-ITT              | Subset of FAS-ITT who were randomised to the anticoagulation domain.                                                                                                                                           |
| ACS-ITT-intermediate | Subset of ACS-ITT who were randomised to intermediate or standard dose only.                                                                                                                                   |
| ACS-ITT-aspirin      | Subset of ACS-ITT who were randomised prior to closure of the standard plus aspirin arm and were eligible for the aspirin arm.                                                                                 |
| ACS-ITT-therapeutic  | Subset of ACS-ITT who were randomised after introduction of the therapeutic dose arm at a site where it became available.                                                                                         |
| ACS-PP               | All participants who were randomised to the anticoagulation domain and satisfied platform, domain, and intervention protocol requirements.                                                                     |

: Overview of the analysis sets used in this report.

\clearpage

### Baseline Characteristics

The following baseline summaries exclude participants who withdrew consent for follow-up.

#### Demographics

The age distribution of participants are presented in @fig-age-overall.

```{r}
#| label: fig-age-overall
#| fig-cap: |
#|   Distribution of age amongst participants randomised to the anticoagulation domain.
knitr::include_graphics(
  "../outputs/figures/baseline/age-overall.pdf"
)
```

Baseline demographics stratified by anticoagulation interventions are reported in @tbl-baseline-demographics.

```{r}
#| label: tbl-baseline-demographics
#| tbl-cap: |
#|   Baseline demographics for participants randomised to the anticoagulation domain.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "baseline", "demographics.tex"))
writeLines(tab[-which(grepl("caption", tab))])
```

#### Co-morbidities

Baseline co-morbidities stratified by anticoagulation interventions are reported in @tbl-baseline-comorbidities.

```{r}
#| label: tbl-baseline-comorbidities
#| tbl-cap: |
#|   Baseline comorbidities for participants randomised to the anticoagulation domain.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "baseline", "comorbidities.tex"))
writeLines(tab[-which(grepl("caption", tab))])
```

#### Prognostics

The relative timing (in days) of hospitalisation, symptom onset, randomisation, and first positive test are presented in @fig-days-to-events-overall.

```{r}
#| label: fig-days-to-events-overall
#| fig-cap: |
#|   Days between events for hospitalisation, randomisation,
#|   symptom onset, and first positive test.
knitr::include_graphics(
  "../outputs/figures/baseline/days-between-events-overall.pdf"
)
```

Baseline prognostics stratified by anticoagulation interventions are reported in @tbl-baseline-prognostics.

```{r}
#| label: tbl-baseline-prognostics
#| tbl-cap: |
#|   Baseline prognostics for participants randomised to the anticoagulation domain.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "baseline", "prognostics.tex"))
writeLines(tab[-which(grepl("caption", tab))])
```

\clearpage

### Discharge Summaries

#### Drugs Received During Hospital Stay

There were 18 participants without a discharge record (due to withdrawal of consent for follow-up). For the continuing participants, the other medications received during their hospital stay are reported in @tbl-discharge-drugs.

```{r}
#| label: tbl-discharge-drugs
#| tbl-cap: |
#|   Drugs received during hospital stay for participants randomised to 
#|   the anti-coagulation domain.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "baseline", "drugs.tex"))
writeLines(tab[-which(grepl("caption", tab))])
```

\clearpage

### Adherence

\clearpage

## Analyses - General

Bayesian models were computed using Stan via `cmdstanr` (0.5.2 and cmdstan version 2.29.2) in R (4.2.0). For each model, 8 chains were used with a warm-up of 1000 iterations and sampling for 2500 iterations per chain resulting in 20,000 posterior draws per model. Standard diagnostics were assessed for each model (divergent transitions, trace plots, R-hat). If an issue was identified (e.g. divergent transitions) then the default sampling parameters may have been adjusted (e.g. increasing target acceptance rate or increasing maximum tree depth). If any convergence issues resulted for the pre-specified models, then they are reported along with the model results. If the model was amended in any way to satisfy convergence criteria (e.g. aggregation of groups, removal of model terms) then this is reported in the relevant section. Sampling was run using a different (randomly selected) random seed for each model, and these were recorded for replication.

Due to the small number of enrolments at New Zealand sites, in models where country of enrolment were included as a term, Australia and New Zealand were combined into one region. The hierarchical site effects for centres in Australia and New Zealand were nested within this joint region rather than each country individually.

For models where site was included as a random effect, sites with less than 5 participants were aggregated within region into an "other sites" grouping. Similarly, for models where epoch was included, epochs with less than 10 participants were aggregated with the adjacent epoch.

Missing outcome data were not imputed for any of the models (with the exception of the deterministic imputation used in the best-case/worst-case sensitivity analyses).

## Trial Decision Criteria

As per the statistical appendix to the core protocol, the following decision quantities were of interest in the anticoagulation domain for the primary outcome model:

-   **Superiority**: superiority is assessed using the posterior probability that the intervention has the lowest odds of the outcome amongst all interventions in the domain. If a single intervention had probability exceeding 0.99 superiority would be triggered for that intervention.
-   **Effectiveness**: effectiveness is assessed relative to the standard dose arm as the posterior probability that the intervention reduces the odds of the outcome. If any intervention had probability exceeding 0.99 than effectiveness would be triggered for that intervention.
-   **Futility**: futility is assessed relative to the standard dose arm as the posterior probability that the intervention reduces the odds of the outcome by no more than a factor of 1/1.1. If any intervention had probability exceeding 0.95 than futility would be triggered for that intervention.
-   **Equivalence**: equivalence is assessed relative to the standard dose arm as the posterior probability that the intervention alters the odds of the outcome by a factor bounded by (1/1.1, 1.1).

\clearpage

## Primary Outcome

The primary outcome is a composite comprised of:

-   day 28 mortality
-   vasopressor/inotropic support within first 28 days
-   new intensive respiratory support within first 28 days.

The definition also allowed for patients who had unknown day 28 status, but were discharged against medical advice (DAMA) and designated as likely to die within 28 days. However, no participants met this criteria (all cases of DAMA and likely to die within 28 days had known day 28 status).

The proportion of participants who met the primary outcome, and rates of missingness, are reported in @tbl-primary-composite-summary. A breakdown of the composite, including missingness by component is reported in @tbl-primary-composite-breakdown. Missingness was predominantly due to unknown patient status at study day 28. Amongst participants where the primary outcome was observed (1,526), 103 (7%) met the primary outcome criteria, most commonly due to requirement of new intensive ventilation and/or death (@tbl-primary-composite-combinations).

A summary of the primary outcome by each of the baseline covariates pre-specified to be included in the primary model (or as pre-specified subgroup analyses) are presented in the appendix (@sec-app-primary-outcome-model-cov).

```{r}
#| label: tbl-primary-composite-summary
#| tbl-cap: |
#|   Summary of primary composite outcome by treatment group.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "anticoagulation-summary.tex"))
writeLines(tab)
```

```{r}
#| label: tbl-primary-composite-breakdown
#| tbl-cap: |
#|   Breakdown of primary composite outcome by treatment group.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "composite-breakdown.tex"))
writeLines(tab)
```

```{r}
#| label: tbl-primary-composite-combinations
#| tbl-cap: |
#|   Breakdown of primary composite combinations by treatment group.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "composite-combinations.tex"))
writeLines(tab)
```

\clearpage

### Primary Analysis (ACS-ITT set)

The primary model was a logistic regression model adjusting for anticoagulation treatment, antiviral treatment, age ($\geq 60$), and region (India (ref), Australia/New Zealand, and Nepal), with random effects for site (nested within country) and epoch (calendar time 4 week intervals, most recent epoch as reference). The three most recent epochs were combined due to small numbers, and the two earliest epochs were combined for the same reason. Sites with fewer than 5 enrolments were combined within region into an "other sites" category.

The primary analysis was based on the ACS-ITT set using the full model as specified in the statistical appendix to the core protocol.

The trial decision quantities are reported in @tbl-primary-model-acs-itt-decision and the model parameter posteriors are summarised in @tbl-primary-model-acs-itt-summary and @fig-primary-model-acs-itt-site-epoch-parameters.

```{r}
#| label: tbl-primary-model-acs-itt-decision
#| tbl-cap: |
#|   Summary of domain decision qauntities (relative to standard dose)
#|   for primary model fit to the ACS-ITT set.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "primary-model-acs-itt-decision-table.tex"))
writeLines(tab)
```

```{r}
#| label: tbl-primary-model-acs-itt-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for primary model fit to the ACS-ITT set.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "primary-model-acs-itt-summary-table.tex"))
writeLines(tab)
```

```{r}
#| label: fig-primary-model-acs-itt-site-epoch-parameters
#| fig-cap: |
#|   Posterior Summaries (point - median, block - 0.75 CrI, line - 0.95 CrI) 
#|   of odds ratio for epoch and site effects for
#|   the primary model fit to the ACS-ITT set.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/primary-model-acs-itt-epoch-site-terms.pdf"
)
```

\clearpage

### Subgroups

The pre-specified subgroups where treatment effect heterogeneity was to be investigate were:

-   region
-   days since symptom onset ($\leq 7$ or $>7$ days)
-   age at enrolment ($<60$ or $\geq 60$ years of age)
-   supplemental oxygen or oxygen saturation less than 94% at randomisation (yes or no)
-   receipt of corticosteroid during hospital stay (yes or no)
-   receipt of remdesivir during hospital stay (yes or no)
-   receipt of other agent intended to be antiviral against SARS-CoV-2 during hospital stay (yes or no)

Domain-specific subgroups were additionally specified as:

-   weight ($< 120$ or $\geq 120$ kg)
-   patient on aspirin at baseline (yes or no)
-   D-dimer above upper limit of normal at baseline (yes or no)

For each sub-group analysis, the primary model was extended to include an interaction term between the covariate of interest and the anticoagulation interventions. In some cases, there may be no information on the subgroup-specific effect (for example, there were no participants in Nepal who were randomised to receive standard dose plus aspirin), but the results are reported in any case noting that the posterior is essentially driven by the prior.

#### Region

A subgroup analysis of region is undertaken using the ACS-ITT set. A summary of the primary outcome by country and intervention is reported in @tbl-descriptive-acs-itt-subgroup-region. Note that no participants enrolled in Nepal or New Zealand received standard dose plus aspirin, and very few in Australia received it, due to the timing of its removal from the domain. Despite this, an interaction term for country and standard dose plus aspirin was retained in the model, however, the associated effect corresponds to the assumed prior given there is no data available.

```{r}
#| label: tbl-descriptive-acs-itt-subgroup-region
#| tbl-cap: |
#|   Summary of participant outcomes by region of enrolment in
#|   the ACS-ITT set.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "primary", 
  "descriptive-acs-itt-subgroup-country-descriptive.tex"))
writeLines(tab)
```

```{r}
#| label: fig-subgroup-acs-itt-region
#| fig-cap: |
#|   Posterior densities of odds ratio for anticoagulation interventions 
#|   relative to standard dose by region subgroup using ACS-ITT set.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/acs-itt-subgroup-country-hte.pdf"
)
```

The primary model was extended to include an interaction between country and anticoagulation intervention.

#### Age group

```{r}
#| label: tbl-descriptive-acs-itt-subgroup-age
#| tbl-cap: |
#|   Summary of participant outcomes by age group at enrolment in
#|   the ACS-ITT set.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "primary", 
  "descriptive-acs-itt-subgroup-age-descriptive.tex"))
writeLines(tab)
```

```{r}
#| label: fig-subgroup-acs-itt-age
#| fig-cap: |
#|   Posterior densities of odds ratio for anticoagulation interventions 
#|   relative to standard dose by age subgroup using ACS-ITT set.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/acs-itt-subgroup-age-hte.pdf"
)
```

#### Days since symptom onset

```{r}
#| label: tbl-descriptive-acs-itt-subgroup-dsfs
#| tbl-cap: |
#|   Summary of participant outcomes by days since symptom onset in
#|   the ACS-ITT set.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "primary", 
  "descriptive-acs-itt-subgroup-dsfs-descriptive.tex"))
writeLines(tab)
```

```{r}
#| label: fig-subgroup-acs-itt-dsfs
#| fig-cap: |
#|   Posterior densities of odds ratio for anticoagulation interventions 
#|   relative to standard dose by days since first symptoms subgroup using 
#|   ACS-ITT set.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/acs-itt-subgroup-dsfs-hte.pdf"
)
```

#### Receipt of Corticosteroids

```{r}
#| label: tbl-descriptive-acs-itt-subgroup-steroids
#| tbl-cap: |
#|   Summary of participant outcomes by receipt of steroids during index
#|   hospital stay in the ACS-ITT set.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "primary", 
  "descriptive-acs-itt-subgroup-steroids-descriptive.tex"))
writeLines(tab)
```

```{r}
#| label: fig-subgroup-acs-itt-steroids
#| fig-cap: |
#|   Posterior densities of odds ratio for anticoagulation interventions 
#|   relative to standard dose by receipt of steroids subgroup using 
#|   ACS-ITT set.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/acs-itt-subgroup-steroids-hte.pdf"
)
```

#### Receipt of Remdesivir

#### D-dimer

#### Weight

Due to smaller numbers (18 participants with weight \> 120 kg and zero events), this pre-specified subgroup analysis was not undertaken.

```{r}
#| label: tbl-descriptive-acs-itt-subgroup-weight
#| tbl-cap: |
#|   Summary of participant outcomes by weight at baseline in the ACS-ITT set.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "primary", 
  "descriptive-acs-itt-subgroup-weight-descriptive.tex"))
writeLines(tab)
```

#### Aspirin

```{r}
#| label: tbl-descriptive-acs-itt-subgroup-aspirin
#| tbl-cap: |
#|   Summary of participant outcomes by whether patient was taking 
#|   aspirin at baseline in the ACS-ITT set.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "primary", 
  "descriptive-acs-itt-subgroup-aspirin-descriptive.tex"))
writeLines(tab)
```

```{r}
#| label: fig-subgroup-acs-itt-aspirin
#| fig-cap: |
#|   Posterior densities of odds ratio for anticoagulation interventions 
#|   relative to standard dose by whether patient taking aspirin using 
#|   ACS-ITT set.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/acs-itt-subgroup-aspirin-hte.pdf"
)
```

\clearpage

### Per-Protocol Analysis

The primary model was re-analysed using the ACS-PP set.

\clearpage

### Sensitivity Analyses

#### Sensitivity: FAS-ITT

The primary model was fit to the expanded FAS-ITT set. The model treatment effects were similar to those obtained under the ACS-ITT set.

```{r}
#| label: tbl-primary-model-fas-itt-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for primary model fit to the FAS-ITT set.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "primary-model-fas-itt-summary-table.tex"))
writeLines(tab)
```

```{r}
#| label: fig-primary-model-fas-itt-site-epoch-parameters
#| fig-cap: |
#|   Posterior Summaries (point - median, block - 75% CrI, line - 95% CrI) 
#|   of odds ratio for epoch and site effects for
#|   the primary model fit to the ACS-ITT set.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/primary-model-fas-itt-epoch-site-terms.pdf"
)
```

\clearpage

#### Sensitivity: Concurrent Randomisations

In the following section, analyses are undertaken where the analysis set is restricted to participants who were randomised concurrently amongst the interventions of interest. Three sets are considered, one for each intervention. Given that the intermediate and standard dose interventions were available the entire time the anticoagulation domain was open, that analysis set is restricted to only participants randomised to one of those interventions. The other sets are determined by a patients calendar time of randomisation. Given that RAR was not activated, the epoch terms are removed from the models. Additionally, due to smaller sample sizes, site effects have been removed from the models. For the definitions of the analysis sets, refer to @sec-analysis-sets.

##### Intermediate dose

-   **Model**: logistic regression
-   **Terms**: anticoagulation intervention, age group, country
-   **Set**: ACS-ITT-intermediate

```{r}
#| label: tbl-primary-composite-acs-itt-c2-summary
#| tbl-cap: |
#|   Summary of primary composite outcome by treatment group for participants in ACS-ITT-intermediate
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "acs-itt-c2-summary.tex"))
writeLines(tab)
```

```{r}
#| label: tbl-primary-model-acs-itt-c2-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for primary model fit to the ACS-ITT-intermediate set.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "primary-model-acs-itt-c2-summary-table.tex"))
writeLines(tab)
```

##### Standard dose plus aspirin

-   **Analysis set**: ACS-ITT where randomisation occurred between 2021-02-08 and 2021-09-10.
-   **Model terms**: anticoagulation intervention, aspirin eligibility, age group, country.

A summary of the number of participants randomised and the number meeting the primary outcome are reported in @tbl-primary-composite-acs-itt-c3-summary, noting that 35 participants were ineligible for the standard dose plus aspirin intervention. The model parameter summaries are reported in @tbl-primary-model-acs-itt-c3-summary.

```{r}
#| label: tbl-primary-composite-acs-itt-c3-summary
#| tbl-cap: |
#|   Summary of primary composite outcome by treatment group for participants in ACS-ITT-aspirin.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "acs-itt-c3-summary.tex"))
writeLines(tab)
```

```{r}
#| label: tbl-primary-model-acs-itt-c3-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for primary model fit to the ACS-ITT-aspirin set.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "primary-model-acs-itt-c3-summary-table.tex"))
writeLines(tab)
```

##### Therapeutic dose

-   **Analysis set**: ACS-ITT where randomisation occurred between 2021-10-14 and 2022-04-08.
-   **Model terms**: anticoagulation intervention, age group, country.

```{r}
#| label: tbl-primary-composite-acs-itt-c4-summary
#| tbl-cap: |
#|   Summary of primary composite outcome by treatment group for participants in ACS-ITT-therapeutic.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "acs-itt-c4-summary.tex"))
writeLines(tab)
```

```{r}
#| label: tbl-primary-model-acs-itt-c4-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for primary model fit to the ACS-ITT-therapeutic set.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "primary-model-acs-itt-c4-summary-table.tex"))
writeLines(tab)
```

\clearpage

#### Sensitivity: Missing meet primary outcome

In this analysis, patients with missing primary outcome data were assumed to have satisfied the primary outcome.

```{r}
#| label: tbl-primary-composite-acs-itt-wost-case-summary
#| tbl-cap: |
#|   Summary of primary composite outcome by treatment group for participants in ACS-ITT set
#|   assuming patients with missing outcomes met the primary outcome.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", 
                           "acs-itt-worst-case-anticoagulation-summary.tex"))
writeLines(tab)
```

```{r}
#| label: tbl-primary-model-acs-itt-wc-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for primary model fit to the ACS-ITT set assuming patients
#|   with missing data met the primary outcome.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "primary-model-acs-itt-worst-case-summary-table.tex"))
writeLines(tab)
```

```{r}
#| label: fig-primary-model-acs-itt-wc-site-epoch-parameters
#| fig-cap: |
#|   Posterior Summaries (point - median, block - 75% CrI, line - 95% CrI) 
#|   of odds ratio for epoch and site effects for
#|   the primary model fit to the ACS-ITT set assuming patients
#|   with missing data met the primary outcome.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/primary-model-acs-itt-worst-case-epoch-site-terms.pdf"
)
```

\clearpage

#### Sensitivity: Missing do not meet primary outcome

In this analysis, patients with missing primary outcome data were assumed to have not satisfied the primary outcome conditions.

```{r}
#| label: tbl-primary-composite-acs-itt-best-case-summary
#| tbl-cap: |
#|   Summary of primary composite outcome by treatment group for participants in ACS-ITT set
#|   assuming patients with missing outcomes did not meet the primary outcome.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", 
                           "acs-itt-best-case-anticoagulation-summary.tex"))
writeLines(tab)
```

```{r}
#| label: tbl-primary-model-acs-itt-bc-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for primary model fit to the ACS-ITT set assuming patients
#|   with missing data did not meet the primary outcome.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "primary-model-acs-itt-best-case-summary-table.tex"))
writeLines(tab)
```

```{r}
#| label: fig-primary-model-acs-itt-bc-site-epoch-parameters
#| fig-cap: |
#|   Posterior Summaries (point - median, block - 75% CrI, line - 95% CrI) 
#|   of odds ratio for epoch and site effects for
#|   the primary model fit to the ACS-ITT set assuming patients
#|   with missing data did not meet the primary outcome.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/primary-model-acs-itt-best-case-epoch-site-terms.pdf"
)
```

\clearpage

### Post-hoc Sensitivity Analyses

The following sections report on other post-hoc analyses which were undertaken, but not explicitly specified in the SAP.

#### Remove site terms

\clearpage

#### Remove epoch terms

\clearpage

#### Remove site and epoch terms

\clearpage

#### Prior Sensitivity

The primary analysis model encodes the prior in terms of orthonormal contrasts. As a check of prior sensitivity, the primary model was re-fit with priors specified in terms of the more usual treatment contrasts.

```{r}
#| label: tbl-primary-model-acs-itt-trt-ctr-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for primary model fit to the ACS-ITT set with priors on treatment conrasts.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "primary", "primary-model-acs-itt-trt-ctr-summary-table.tex"))
writeLines(tab)
```

```{r}
#| label: fig-primary-model-acs-itt-trt-ctr-site-epoch-parameters
#| fig-cap: |
#|   Posterior Summaries (point - median, block - 0.75 CrI, line - 0.95 CrI) 
#|   of odds ratio for epoch and site effects for
#|   the primary model fit to the ACS-ITT set with priors on treatment conrasts.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/primary-model-acs-itt-trt-ctr-epoch-site-terms.pdf"
)
```

\clearpage

## Secondary Outcomes

For all secondary outcomes, the primary model (adjusting for interventions, age group, country, site, and epoch using the relevant outcome model) was fit to the ACS-ITT set. The only sensitivity analysis conducted was to repeat the analyses restricted to contemporaneous controls without the epoch term.

### Time to clinical recovery

```{r}
#| label: fig-7-1-descriptive
#| fig-cap: |
#|   Observed progression of patients with respect to death and recovery.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/outcome-7-1-descriptive.pdf"
)
```

\clearpage

### WHO 8-point ordinal outcome scale at day 28

```{r}
#| label: fig-7-2-descriptive
#| fig-cap: |
#|   Observed distribution of WHO outcome scale at day 28 by treatment group.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/outcome-7-2-descriptive.pdf"
)
```

\clearpage

#### Sensitivity: Concurrent Enrolments

\clearpage

### All-cause mortality

This section reports on the analysis of the secondary outcome: all-cause mortality to day 28. For this outcome, participants who died within 28 days were coded to have a value of 1, and those who did not, to have a value of 0. The model is coded so that an odds ratio less than 1 implies a benefit (reduction in odds of death by day 28).

-   **Model**: logistic regression
-   **Terms**: anticoagulation intervention, antiviral intervention, aspirin eligibility, age group, region, site nested within region, and epoch.
-   **Set**: ACS-ITT

@tbl-7-3-summary presents the number of participants where the outcome was observed by the allocated anticoagulation arm. The model parameters (odds ratios) are summarised in @tbl-7-3-primary-model-acs-itt-summary for the fixed-effect terms and in @fig-7-3-primary-model-acs-itt-site-epoch-parameters for the site and epoch specific terms.

The proportion who had died by day 28 was 3.3% (50 / 1530) amongst all randomised participants. Compared with standard dose, the median adjusted odds ratios (95% CrI) from the primary model were: 0.84 (0.42, 1.69) for intermediate dose, 0.81 (0.36, 1.82) for standard dose plus aspirin, and 3.17 (0.94, 10.3) for therapeutic dose. The corresponding posterior probabilities for effectiveness were 0.69, 0.69 and 0.03 respectively.  

```{r}
#| label: tbl-7-3-summary
#| tbl-cap: |
#|   Summary of mortality by day 28 by treatment group.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary", "anticoagulation-summary-mortality.tex"))
writeLines(tab)
```

```{r}
#| label: tbl-7-3-primary-model-acs-itt-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for mortality by day 28 primary model fit to the ACS-ITT set.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "secondary", "7-3-primary-model-acs-itt-summary-table.tex"))
writeLines(tab)
```

```{r}
#| label: fig-7-3-primary-model-acs-itt-site-epoch-parameters
#| fig-cap: |
#|   Posterior Summaries (point - median, block - 75% CrI, line - 95% CrI) 
#|   of odds ratio for epoch and site effects on day 28 mortality for
#|   the primary model fit to the ACS-ITT set.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-3-primary-model-epoch-site-terms.pdf"
)
```

\clearpage

#### Sensitivity: Concurrent Enrolments

##### Intermediate dose

-   **Model**: logistic regression
-   **Terms**: anticoagulation intervention, age group, region
-   **Set**: ACS-ITT-intermediate

```{r}
#| label: tbl-7-3-concurrent-intermediate-summary
#| tbl-cap: |
#|   Summary of mortality to day 28 by treatment group.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary",
  "7-3-anticoagulation-concurrent-intermediate-summary.tex"))
writeLines(tab)
```

```{r}
#| label: tbl-7-3-concurrent-intermediate-model-summary
#| tbl-cap: |
#|   Summary of posterior odds ratios for intermediate dose concurrent set.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary",
  "7-3-primary-model-acs-itt-concurrent-intermediate-summary-table.tex"))
writeLines(tab)
```

##### Standard dose plus aspirin

-   **Model**: logistic regression
-   **Terms**: anticoagulation intervention, age group, region
-   **Set**: ACS-ITT-aspirin aspirin arm

```{r}
#| label: tbl-7-3-concurrent-stdaspirin-summary
#| tbl-cap: |
#|   Summary of mortality to day 28 by treatment group.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary",
  "7-3-anticoagulation-concurrent-stdaspirin-summary.tex"))
writeLines(tab)
```

```{r}
#| label: tbl-7-3-concurrent-stdaspirin-model-summary
#| tbl-cap: |
#|   Summary of posterior odds ratios for standard dose plus aspirin concurrent set.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary",
  "7-3-primary-model-acs-itt-concurrent-stdaspirin-summary-table.tex"))
writeLines(tab)
```

##### Therapeutic dose

-   **Model**: logistic regression
-   **Terms**: anticoagulation intervention, age group, region
-   **Set**: ACS-ITT-therapeutic

*Note: the reference region was switched to Nepal for this model due to small numbers in India.*

```{r}
#| label: tbl-7-3-concurrent-therapeutic-summary
#| tbl-cap: |
#|   Summary of mortality to day 28 by treatment group.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary",
  "7-3-anticoagulation-concurrent-therapeutic-summary.tex"))
writeLines(tab)
```

```{r}
#| label: tbl-7-3-concurrent-therapeutic-model-summary
#| tbl-cap: |
#|   Summary of posterior odds ratios for therapeutic dose concurrent set.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary",
  "7-3-primary-model-acs-itt-concurrent-therapeutic-summary-table.tex"))
writeLines(tab)
```

\clearpage

### Days alive and free of hospital

This section reports on the analysis of the secondary outcome: days alive and free of hospital (DAFH) to day 28. For this outcome, participants who died within 28 days were coded have have 0 DAFH. The model is coded so that an odds ratio greater than 1 implies a beneift (more days alive and free of hospital).

-   **Model**: cumulative logistic (ordinal) regression assuming proportional odds
-   **Terms**: anticoagulation intervention, antiviral intervention, aspirin eligibility, age group, region, site nested within region, and epoch.
-   **Set**: ACS-ITT

@tbl-7-4-summary presents the number of participants where the outcome was observed by the allocated anticoagulation arm. The observed distribution of DAFH by arm is shown in @fig-7-4-dist-overall, @fig-7-4-descriptive, and @fig-7-4-descriptive2. The model parameters (odds ratios) are summarised in @tbl-7-4-primary-model-acs-itt-summary for the fixed-effect terms and in @fig-7-4-primary-model-acs-itt-site-epoch-parameters for the site and epoch specific terms.

The median (IQR) DAFH was 23 (21 - 24) days amongst all randomised participants. Compared with standard dose, the median adjusted odds ratios (95% CrI) from the primary model were 1.18 (0.98, 1.42) for intermediate dose, 1.10 (0.86, 1.41) for standard dose plus aspirin, and 0.75 (0.48, 1.16) for therapeutic dose. The corresponding posterior probabilities for effectiveness were 0.96, 0.79 and 0.10 respectively.

```{r}
#| label: tbl-7-4-summary
#| tbl-cap: |
#|   Summary of days alive and free of hospital to day 28 by treatment group.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary", "7-4-anticoagulation-summary.tex"))
writeLines(tab)
```

```{r}
#| label: fig-7-4-dist-overall
#| fig-cap: |
#|   Observed overall distribution of days alive and free of hospital at day 28.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/outcome-7-4-dist-overall.pdf"
)
```

```{r}
#| label: fig-7-4-descriptive
#| fig-cap: |
#|   Observed distribution of days alive and free of hospital at day 28 by treatment group.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/outcome-7-4-descriptive.pdf"
)
```

```{r}
#| label: fig-7-4-descriptive2
#| fig-cap: |
#|   Observed cumulative distribution of days alive and free of hospital at day 28 by treatment group.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/outcome-7-4-descriptive2.pdf"
)
```

```{r}
#| label: tbl-7-4-primary-model-acs-itt-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for days alive and free of hospital to day 28 primary model fit to the ACS-ITT set.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "secondary", "7-4-primary-model-acs-itt-summary-table.tex"))
writeLines(tab)
```

```{r}
#| label: fig-7-4-primary-model-acs-itt-site-epoch-parameters
#| fig-cap: |
#|   Posterior Summaries (point - median, block - 75% CrI, line - 95% CrI) 
#|   of odds ratio for epoch and site effects on days alive and free of 
#|   hospital to day 28 for the primary model fit to the ACS-ITT set.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-4-primary-model-epoch-site-terms.pdf"
)
```

\clearpage

#### Sensitivity: Concurrent Enrolments

##### Intermediate dose

-   **Model**: cumulative logistic (ordinal) regression assuming proportional odds
-   **Terms**: anticoagulation intervention, age group, region
-   **Set**: ACS-ITT-intermediate

```{r}
#| label: tbl-7-4-concurrent-intermediate-summary
#| tbl-cap: |
#|   Summary of days alive and free of hospital to day 28 by treatment group.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary", "7-4-anticoagulation-concurrent-intermediate-summary.tex"))
writeLines(tab)
```

```{r}
#| label: fig-7-4-descriptive-concurrent-intermediate
#| fig-cap: |
#|   Observed distribution of days alive and free of hospital at day 28 by treatment group.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/outcome-7-4-descriptive-concurrent-intermediate.pdf"
)
```

```{r}
#| label: tbl-7-4-concurrent-intermediate-model-summary
#| tbl-cap: |
#|   Summary of days alive and free of hospital to day 28 by treatment group.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary", "7-4-primary-model-acs-itt-concurrent-intermediate-summary-table.tex"))
writeLines(tab)
```

##### Standard dose plus aspirin

-   **Model**: cumulative logistic (ordinal) regression assuming proportional odds
-   **Terms**: anticoagulation intervention, age group, region
-   **Set**: ACS-ITT-aspirin

```{r}
#| label: tbl-7-4-concurrent-stdaspirin-summary
#| tbl-cap: |
#|   Summary of days alive and free of hospital to day 28 by treatment group.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary", "7-4-anticoagulation-concurrent-stdaspirin-summary.tex"))
writeLines(tab)
```

```{r}
#| label: fig-7-4-descriptive-concurrent-stdaspirin
#| fig-cap: |
#|   Observed distribution of days alive and free of hospital at day 28 by treatment group.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/outcome-7-4-descriptive-concurrent-stdaspirin.pdf"
)
```

```{r}
#| label: tbl-7-4-concurrent-stdaspirin-model-summary
#| tbl-cap: |
#|   Summary of days alive and free of hospital to day 28 by treatment group.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary", "7-4-primary-model-acs-itt-concurrent-stdaspirin-summary-table.tex"))
writeLines(tab)
```

##### Therapeutic dose

-   **Model**: cumulative logistic (ordinal) regression assuming proportional odds
-   **Terms**: anticoagulation intervention, age group, region
-   **Set**: ACS-ITT-therapeutic

*Note: the reference region was switched to Nepal for this model due to small numbers in India.*

```{r}
#| label: tbl-7-4-concurrent-therapeutic-summary
#| tbl-cap: |
#|   Summary of days alive and free of hospital to day 28 by treatment group.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary", "7-4-anticoagulation-concurrent-therapeutic-summary.tex"))
writeLines(tab)
```

```{r}
#| label: fig-7-4-descriptive-concurrent-therapeutic
#| fig-cap: |
#|   Observed distribution of days alive and free of hospital at day 28 by treatment group.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/outcome-7-4-descriptive-concurrent-therapeutic.pdf"
)
```

```{r}
#| label: tbl-7-4-concurrent-therapeutic-model-summary
#| tbl-cap: |
#|   Summary of days alive and free of hospital to day 28 by treatment group.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary", "7-4-primary-model-acs-itt-concurrent-therapeutic-summary-table.tex"))
writeLines(tab)
```

\clearpage

### Days alive and free of invasive or non-invasive ventilation (DAFV)

This section reports on the analysis of the secondary outcome: days alive and free invasive or non-invasive ventilation (DAFV) to day 28. For this outcome, participants who died within 28 days were coded have have 0 DAFV.

-   **Model**: cumulative logistic (ordinal) regression assuming proportional odds
-   **Terms**: anticoagulation intervention, antiviral intervention, aspirin eligibility, age group, region, site nested within region, and epoch.
-   **Set**: ACS-ITT

@tbl-7-5-summary presents the number of participants where the outcome was observed by the allocated anticoagulation arm. The observed distribution of DAFH by arm is shown in @fig-7-5-descriptive.

```{r}
#| label: tbl-7-5-summary
#| tbl-cap: |
#|   Summary of days alive and free of ventilation to day 28 by treatment group.
#| results: asis
tab <- readLines(file.path(
  "..", "outputs", "tables", "outcomes", "secondary", "7-5-anticoagulation-summary.tex"))
writeLines(tab)
```

```{r}
#| label: fig-7-5-descriptive
#| fig-cap: |
#|   Observed distribution of days alive and free of ventilation at day 28 by treatment group.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/outcome-7-5-descriptive.pdf"
)
```

\clearpage

#### Sensitivity: Concurrent Enrolments

\clearpage

### Presence of patient reported outcome of shortness of breath

\clearpage

#### Sensitivity: Concurrent Enrolments

\clearpage

### Modified Medical Research Council (mMRC) breathlessness scale

\clearpage

#### Sensitivity: Concurrent Enrolments

\clearpage

### Quality of life as measured by EQ-5D-5L questionnaire

\clearpage

## Domain Specific Outcomes

The anticoagulation domain-specific outcomes are reported in @tbl-8-0-acs-itt-summary. The number of thrombotic and bleeding events were low across all interventions and overall.

```{r}
#| label: tbl-8-0-acs-itt-summary
#| tbl-cap: |
#|   Descriptive summary of anticoagulation-specific outcomes
#|   (thrombotic and bleeding events).
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "secondary", "8-0-anticoagulation-specific-summary.tex"))
writeLines(tab)
```

The SAP described a formal analysis of the two composite outcomes: any thrombotic event (or death), and any clinical relevant bleeding. Due to the small number of bleeding events (6 of 1,521 known outcomes) this analysis was not undertaken. Similarly, for any thrombotic event or death, due to the majority of the events being due to death, the results were expected to be similar to those for all-cause mortality to day 28. Despite this, the analysis *was* performed for any thrombotic event or death and the results reported below.

### Any thrombotic event (or death) to day 28

```{r}
#| label: tbl-8-1-primary-model-acs-itt-summary
#| tbl-cap: |
#|   Summary of model parameters (fixed-effects odds-ratios) 
#|   for any thrombotic event or death to day 28 
#|   for primary model fit to the ACS-ITT set.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "outcomes", "secondary", "8-1-primary-model-acs-itt-summary-table.tex"))
writeLines(tab)
```

```{r}
#| label: fig-8-1-primary-model-acs-itt-site-epoch-parameters
#| fig-cap: |
#|   Posterior Summaries (point - median, block - 75% CrI, line - 95% CrI) 
#|   of odds ratio for epoch and site effects for any thrombotic event or death
#|   to day 28 for the primary model fit to the ACS-ITT set.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/8-1-primary-model-epoch-site-terms.pdf"
)
```

\clearpage

# Appendix

## Primary Outcome by Model Covariates (ACS-ITT) {#sec-app-primary-outcome-model-cov}

```{r}
#| label: fig-primary-outcome-age
#| fig-cap: |
#|   Proportion of participants satisfying primary outcome criteria
#|   by age at randomisation. Vertical dashed line indicates the 
#|   pre-specified cut-point of 60 years of age.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/outcome-age.pdf"
)
```

```{r}
#| label: fig-primary-outcome-country
#| fig-cap: |
#|   Proportion of participants satisfying primary outcome criteria
#|   by country of randomisation.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/outcome-country.pdf"
)
```

```{r}
#| label: fig-primary-outcome-country-site
#| fig-cap: |
#|   Proportion of participants satisfying primary outcome criteria
#|   by country and site of randomisation.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/outcome-country-site.pdf"
)
```

```{r}
#| label: fig-primary-outcome-calendar-time
#| fig-cap: |
#|   Proportion of participants satisfying primary outcome criteria
#|   by calendar time (month) of randomisation.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/outcome-calendar-time.pdf"
)
```

```{r}
#| label: fig-primary-outcome-dsfs
#| fig-cap: |
#|   Proportion of participants satisfying primary outcome criteria
#|   by days since first symptoms at randomisation. 
#|   Vertical dashed line indicates the pre-specified cut-point of 7 days.
knitr::include_graphics(
  "../outputs/figures/outcomes/primary/outcome-dsfs.pdf"
)
```

\clearpage

## Time to recovery to day 28 by model covariates (ACS-ITT) {#sec-app-7-1-model-cov}

\clearpage

## WHO outcome scale at day 28 by model covariates (ACS-ITT) {#sec-app-7-2-model-cov}

```{r}
#| label: fig-7-2-age
#| fig-cap: |
#|   Distribution of WHO outcome scale day 28
#|   by age at randomisation. Vertical dashed line indicates the 
#|   pre-specified cut-point of 60 years of age.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-2-age.pdf"
)
```

```{r}
#| label: fig-7-2-country
#| fig-cap: |
#|   Distribution of WHO scale at day 28
#|   by country of randomisation.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-2-country.pdf"
)
```

```{r}
#| label: fig-7-2-country-site
#| fig-cap: |
#|   Distribution of WHO scale at day 28
#|   by country and site of randomisation.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-2-country-site.pdf"
)
```

```{r}
#| label: fig-7-2-calendar-time
#| fig-cap: |
#|   Distribution of WHO scale at day 28
#|   by calendar time (month) of randomisation.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-2-calendar-time.pdf"
)
```

\clearpage

## Mortality to day 28 by Model Covariates (ACS-ITT) {#sec-app-7-3-model-cov}

```{r}
#| label: fig-7-3-age
#| fig-cap: |
#|   Proportion of participants who died by day 28
#|   by age at randomisation. Vertical dashed line indicates the 
#|   pre-specified cut-point of 60 years of age.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-3-age.pdf"
)
```

```{r}
#| label: fig-7-3-country
#| fig-cap: |
#|   Proportion of participants who died by day 28
#|   by country of randomisation.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-3-country.pdf"
)
```

```{r}
#| label: fig-7-3-country-site
#| fig-cap: |
#|   Proportion of participants who died by day 28
#|   by country and site of randomisation.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-3-country-site.pdf"
)
```

```{r}
#| label: fig-7-3-calendar-time
#| fig-cap: |
#|   Proportion of participants who died by day 28
#|   by calendar time (month) of randomisation.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-3-calendar-time.pdf"
)
```

\clearpage

## Days alive and free of hospital to day 28 by Model Covariates (ACS-ITT) {#sec-app-7-4-model-cov}

```{r}
#| label: fig-7-4-age
#| fig-cap: |
#|   Distribution of days alive and free of hospital to day 28
#|   by age groups.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-4-age.pdf"
)
```

```{r}
#| label: fig-7-4-country
#| fig-cap: |
#|   Distribution of days alive and free of hospital to day 28
#|   by country of randomisation.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-4-country.pdf"
)
```

```{r}
#| label: fig-7-4-country-site
#| fig-cap: |
#|   Distribution of days alive and free of hospital to day 28
#|   by country and site of randomisation.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-4-country-site.pdf"
)
```

```{r}
#| label: fig-7-4-calendar-time
#| fig-cap: |
#|   Distribution of days alive and free of hospital to day 28
#|   by calendar time (month) of randomisation.
knitr::include_graphics(
  "../outputs/figures/outcomes/secondary/7-4-calendar-time.pdf"
)
```

\clearpage

## Days alive and free of ventilation to day 28 by Model Covariates (ACS-ITT) {#sec-app-7-5-model-cov}

\clearpage

## Posterior Predictive - Primary Model ACS-ITT

```{r}
#| label: fig-primary-model-acs-itt-ppc
#| fig-cap: |
#|   Posterior predictive distribution for primary outcome 
#|   by model covariates for primary model using ACS-ITT.
#|   Vertical red line indicates observed proportions.
pth <- file.path("..", "outputs", "figures", "outcomes", "primary",
                 "primary-model-acs-itt-ppc.pdf")
knitr::include_graphics(pth)
```
