---
title: "ASCOT Anticoagulation Clinical Study Report"
date: '2022-06-30'
author:
  - name: James Totterdell
    affiliation: University of Sydney
  - name: Rob Mahar
    affiliation: University of Melbourne
format:
  pdf:
    documentclass: scrreprt
    toc: true
    number-sections: true
    colorlinks: true
    lof: true
    lot: true
    mainfont: TeX Gyre Pagella
    mathfont: TeX Gyre Pagella Math
    monofont: TeX Gyre Cursor
    sansfont: TeX Gyre Heros
    include-in-header:
      - packages.tex
execute: 
  echo: false
---

# Synopsis

# Results

## Study Population

At the time of database lock for the anti-coagulation domain, ... participants had been enrolled onto the study platform and ... participants had been randomised to the anticoagulation domain. The first patient was randomised on ... and the last patient enrolled into the anticoagulation domain was randomised on... .

### Disposition

Platform and domain specific flow diagrams are included in ...

@fig-enrolments presents platform enrolments over time with timing of intervention availabilities.

```{r}
#| label: fig-enrolments
#| fig-cap: |
#|   Overall enrolment to platform and intervention availability.
knitr::include_graphics(
  "../outputs/figures/baseline/enrolment-overall.pdf"
)
```


### Deviations

{{< pagebreak >}}

### Baseline Characteristics

Baseline demographics are stratified by the anti-coagulation interventions are reported in @tbl-baseline-demographics
```{r}
#| label: tbl-baseline-demographics
#| tbl-cap: |
#|   Baseline demographics for participants randomised to the anti-coagulation domain.
#| results: asis
tab <- readLines(file.path("..", "outputs", "tables", "baseline", "demographics.tex"))
writeLines(tab[-which(grepl("caption", tab))])
```


### Adherence

## Primary Outcome 

## Secondary Outcomes

### Time to clinical recovery

### All-cause mortality

### WHO outcome scale

### Days free of hospitalisation

## Domain Specific Outcomes

## Safety

# Appendices {.unnumbered}
