---
title: "WHO 8-point Outcome Scale"
description: |
  Working analyses of the WHO 8-point outcome scale outcome.
author: "James Totterdell"
date: last-modified
format: 
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    captions: true
    cap-location: margin
    table-captions: true
    tbl-cap-location: margin
    reference-location: margin
    theme: journal
    fontsize: 1em
    self-contained: true
    standalone: true
    code-tools: true
    code-fold: true
    code-link: false

execute:
  warning: false
  message: false
  echo: true

engine: knitr
---

# Preamble {#preamble}

```{r}
#| label: pkgs
#| code-summary: Load packages
library(tidyverse)
library(labelled)
library(kableExtra)
library(rstan)
library(posterior)
library(bayestestR)
library(bayesplot)
library(matrixStats)

theme_set(theme_minimal(base_size = 11))
```

```{r}
logit <- function(x) log(x) - log(1 - x)
expit <- function(x) 1 / (1 + exp(-x))
ordered_logit <- function(x) {
  c(
    1 - expit(-x[1]),
    expit(-x[1:(length(x)-1)]) - expit(-x[2:(length(x))]),
    expit(-tail(x, 1))
  )
}
```

```{r}
#| label: data
#| code-summary: Prepare dataset
source("r/derive_full_datasets.r")
dat <- read_all_no_daily()
```

## Descriptive {#descriptive}

### Day 28

```{r}
ovr_counts <- dat %>%
  filter(ENR_rec == 1, WTH_FU == 0, ACS_ITT == 1) %>%
  dplyr::count(D28_who, D28_death) %>%
  mutate(
    p = n / sum(n),
    p_ex_miss = c(n[!is.na(D28_who)] / sum(n * !is.na(D28_who)), NA)
  )
trt_counts <- dat %>%
  filter(ENR_rec == 1, WTH_FU == 0, ACS_ITT == 1, !is.na(D28_who)) %>%
  dplyr::count(CAssignment, D28_who = factor(as.integer(D28_who))) %>%
  complete(CAssignment, D28_who, fill = list(n = 0)) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n))
ovr_counts
```

```{r}
dat %>%
  filter(ENR_rec == 1, WTH_FU == 0, ACS_ITT == 1) %>%
  dplyr::count(CAssignment, D28_who, D28_death) %>%
  spread(CAssignment, n, fill = 0)
```

```{r}
dat %>%
  filter(ENR_rec == 1, WTH_FU == 0, ACS_ITT == 1, !is.na(D28_who)) %>%
  dplyr::count(CAssignment, D28_who = factor(as.integer(D28_who))) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n)) %>%
  ggplot(., aes(CAssignment, p)) +
  geom_col(aes(fill = D28_who)) +
  scale_fill_viridis_d(option = "B")
```

```{r}
dat %>%
  filter(ENR_rec == 1, WTH_FU == 0, ACS_ITT == 1, !is.na(D28_who)) %>%
  dplyr::count(CAssignment, D28_who = factor(as.integer(D28_who))) %>%
  complete(CAssignment, D28_who, fill = list(n = 0)) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n)) %>%
  ggplot(., aes(D28_who, p)) +
  facet_wrap( ~ CAssignment) +
  geom_point() +
  geom_segment(aes(xend = D28_who, y = 0, yend = p))
```

#### Sample Cumulative Logits

Proportional odds looks reasonable for all logits except 1.

```{r}
trt_counts %>% 
  group_by(CAssignment) %>% 
  mutate(clogit = logit(cumsum(p))) %>%
  group_by(D28_who) %>%
  mutate(rel_clogit = clogit - mean(clogit)) %>%
  filter(D28_who != 8) %>%
  ggplot(., aes(CAssignment, rel_clogit)) +
  facet_wrap( ~ D28_who) +
  geom_point() +
  labs(y = "Relative (to mean) sample cumulative logit")
```

## Modelling (Day 28) {#modelling}

### Primary Model

### Simplified (Treatment Only)

```{r}
#| label: fit-simple-model
#| code-summary: Fit simple model (treatment only)
seed <- 81350
mod <- stan_model("stan/logistic_cumulative_ordinal.stan")

mdat <- dat %>%
  filter(ENR_rec == 1, WTH_FU == 0, ACS_ITT == 1, !is.na(D28_who)) %>%
  select(CAssignment, D28_who)

C <- contr.orthonorm(4)
X <- model.matrix(
  ~ CAssignment, 
  data = mdat, 
  contrast = list(CAssignment = contr.orthonorm))[, -1]
y <- as.integer(mdat$D28_who)
N <- nrow(X)
K <- ncol(X)
J <- max(y)
beta_sd <- rep(1, K)
p_par <- rep(1 / J, J)

sdat <- list(
  N = N, K = K, J = J, X = X, y = y, beta_sd = beta_sd, p_par = p_par
)

snk <- capture.output(mfit <- mod$sample(
  data = sdat,
  seed = seed,
  refresh = 0,
  iter_sampling = 2500,
  chains = 8,
  parallel_chains = 8
))
```

```{r}
#| label: fit-simple-samples
#| code-summary: Get posterior draws

p_rvar <- as_draws_rvars(mfit$draws("p"))$p
a_rvar <- as_draws_rvars(mfit$draws("alpha"))$alpha
b_rvar <- as_draws_rvars(mfit$draws("beta"))$beta

b_uncon_rvar <- C %**% b_rvar
b_trt_rvar <- transform_coding(C, contr.treatment(4)) %**% b_rvar

# Treatment specific level probabilities
p_C1 <- ordered_logit(a_rvar - b_uncon_rvar[1])
p_C2 <- ordered_logit(a_rvar - b_uncon_rvar[2])
p_C3 <- ordered_logit(a_rvar - b_uncon_rvar[3])
p_C4 <- ordered_logit(a_rvar - b_uncon_rvar[4])
p_df <- expand_grid(
  CAssignment = c("C1", "C2", "C3", "C4"),
  who = 1:8
) %>%
  mutate(
    p = c(p_C1, p_C2, p_C3, p_C4),
    med = median(p),
    lo = quantile(p, prob = 0.025)[1, ],
    hi = quantile(p, prob = 0.975)[1, ]
  )
```

```{r}
#| label: fig-model-simple-versus-observed
#| code-summary: Compare model level probabilities to observed
#| fig-cap: |
#|   Posterior probability of outcome levels by treatment group
#|   compared to observed proportions.
obs <- dat %>%
  filter(ENR_rec == 1, WTH_FU == 0, ACS_ITT == 1, !is.na(D28_who)) %>%
  dplyr::count(CAssignment, D28_who = as.integer(D28_who)) %>%
  complete(CAssignment, D28_who, fill = list(n = 0)) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n))

ggplot(p_df, aes(who + 0.1, med)) +
  facet_wrap( ~ CAssignment) +
  geom_pointrange(aes(ymin = lo, ymax = hi), fatten = 1, colour = "red") +
  geom_point(data = obs, aes(D28_who - 0.1, p), shape = 10) +
  labs(
    x = "WHO outcome scale",
    y = "Probability of outcome"
  )
```

#### Non-proportional odds

There is evidence of non-proportional odds with respect to the first logit. This is explored below. In this model, the first logit has a distinct parameter, but all other logits share a parameter.

```{r}
#| label: fig-model-simple-nonprop-odds
#| code-summary: Compare non-proportional odds model
#| fig-cap: |
#|   Compare posterior logits assuming proportional odds and 
#|   non-proportional odds at the first logit only.
seed <- 81350
modagg <- stan_model("stan/logistic_cumulative_ordinal_agg.stan")
modagg1nprop <- stan_model("stan/logistic_cumulative_ordinal_1nonprop.stan")

mdatagg <- mdat %>%
  dplyr::count(CAssignment, D28_who) %>%
  spread(D28_who, n, fill = 0) %>%
  rowwise() %>%
  mutate(n = sum(across(2:9, ~ .))) %>%
  ungroup()

X <- model.matrix(
  ~ CAssignment, 
  data = mdatagg, 
  contrast = list(CAssignment = contr.orthonorm))[, -1]
y <- as.matrix(mdatagg[, 2:9])
n <- mdatagg$n
N <- nrow(X)
K <- ncol(X)
J <- ncol(y)
beta_sd <- rep(1, K)
p_par <- rep(1 / J, J)

sdat <- list(
  N = N, K = K, J = J, 
  X = X, y = y, n = n, 
  beta_sd = beta_sd, p_par = p_par
)

snk <- capture.output(mfitagg <- modagg$sample(
  data = sdat,
  seed = seed,
  refresh = 0,
  iter_sampling = 2500,
  chains = 8,
  parallel_chains = 8
))

snk <- capture.output(mfitaggnp <- modagg1nprop$sample(
  data = sdat,
  seed = seed,
  refresh = 0,
  iter_sampling = 2500,
  chains = 8,
  parallel_chains = 8
))

beta_rvar <- as_draws_rvars(mfitagg$draws("beta"))$beta
np_beta_rvar <- as_draws_rvars(mfitaggnp$draws("beta"))$beta
np_beta1_rvar <- as_draws_rvars(mfitaggnp$draws("beta1"))$beta1

b_uncon_rvar <- C %**% beta_rvar
np_b_uncon_rvar <- C %**% np_beta_rvar
np_b1_uncon_rvar <- C %**% np_beta1_rvar

b_trt_rvar <- transform_coding(C, contr.treatment(4)) %**% beta_rvar
np_b1_trt_rvar <- transform_coding(C, contr.treatment(4)) %**% np_beta_rvar
np_b_trt_rvar <- transform_coding(C, contr.treatment(4)) %**% np_beta1_rvar

pdat <- expand_grid(
  D28_who = 1:7,
  CAssignment = c("C1", "C2", "C3", "C4")
) %>%
  mutate(
    clogit = rep(-b_uncon_rvar, times = 7),
    clogit_np = c(-np_b1_uncon_rvar, rep(-np_b_uncon_rvar, times = 6))
  )

ggplot(pdat,
       aes(CAssignment, y = median(clogit))) +
  facet_wrap( ~ D28_who) +
  geom_pointrange(aes(
    ymin = quantile(clogit, 0.025)[1, ],
    ymax = quantile(clogit, 0.975)[1, ],
    colour = "Prop odds"),
    fatten = 1,
    position = position_nudge(x = -0.1)) +
  geom_pointrange(aes(
    y = median(clogit_np),
    ymin = quantile(clogit_np, 0.025)[1, ],
    ymax = quantile(clogit_np, 0.975)[1, ],
    colour = "Non-prop odds"),
    fatten = 1,
    position = position_nudge(x = 0.1)) +
  geom_point(data = trt_counts %>% 
    group_by(CAssignment) %>% 
    mutate(clogit = logit(cumsum(p))) %>%
    group_by(D28_who) %>%
    mutate(rel_clogit = clogit - mean(clogit)) %>%
    filter(D28_who != 8),
    aes(CAssignment, rel_clogit, colour = "Observed")) +
  scale_colour_manual(
    "Model", 
    values = c(
      "Observed" = "black",
      "Prop odds" = "blue", 
      "Non-prop odds" = "red")) +
  labs(y = "Outcome specific logit\nposterior median and 95%C")
```

```{r}
#| label: fig-model-simple-nonprop-odds-probs
#| code-summary: Compare non-proportional odds model probabilities
#| fig-cap: |
#|   Compare posterior summaries for outcome level probabilities 
#|   assuming proportional odds and non-proportional odds at 
#|   the first logit only.
alpha_rvar <- as_draws_rvars(mfitagg$draws("alpha"))$alpha
alphanp_rvar <- as_draws_rvars(mfitaggnp$draws("alpha"))$alpha

p_C1 <- ordered_logit(alpha_rvar - b_uncon_rvar[1])
p_C2 <- ordered_logit(alpha_rvar - b_uncon_rvar[2])
p_C3 <- ordered_logit(alpha_rvar - b_uncon_rvar[3])
p_C4 <- ordered_logit(alpha_rvar - b_uncon_rvar[4])

pnp_C1 <- ordered_logit(
  c(alphanp_rvar[1] - np_b1_uncon_rvar[1],
    alphanp_rvar[-1] - np_b_uncon_rvar[1]
))
pnp_C2 <- ordered_logit(
  c(alphanp_rvar[1] - np_b1_uncon_rvar[2],
    alphanp_rvar[-1] - np_b_uncon_rvar[2]
))
pnp_C3 <- ordered_logit(
  c(alphanp_rvar[1] - np_b1_uncon_rvar[3],
    alphanp_rvar[-1] - np_b_uncon_rvar[3]
))
pnp_C4 <- ordered_logit(
  c(alphanp_rvar[1] - np_b1_uncon_rvar[4],
    alphanp_rvar[-1] - np_b_uncon_rvar[4]
))

p_df <- expand_grid(
  CAssignment = c("C1", "C2", "C3", "C4"),
  who = 1:8
) %>%
  mutate(
    p = c(p_C1, p_C2, p_C3, p_C4),
    pnp = c(pnp_C1, pnp_C2, pnp_C3, pnp_C4)
  )

ggplot(p_df, aes(who, mean(p))) +
  facet_wrap( ~ CAssignment) +
    geom_pointrange(aes(
    ymin = quantile(p, 0.025)[1, ],
    ymax = quantile(p, 0.975)[1, ],
    colour = "Prop odds"),
    fatten = 1,
    position = position_nudge(x = -0.15)) +
  geom_pointrange(aes(
    y = mean(pnp),
    ymin = quantile(pnp, 0.025)[1, ],
    ymax = quantile(pnp, 0.975)[1, ],
    colour = "Non-prop odds"),
    fatten = 1,
    position = position_nudge(x = 0.15)) +
  geom_point(data = obs, aes(D28_who, p)) +
  labs(
    x = "WHO outcome scale",
    y = "Posterior mean and 95% CrI for outcome probability"
  )+
  scale_colour_manual(
    "Model", 
    values = c(
      "Observed" = "black",
      "Prop odds" = "blue", 
      "Non-prop odds" = "red"))
```
