---
title: "Data crosschecks"
description: |
  Cross check of D28 data.
author: 
  - name: James Totterdell
    affiliation: University of Sydney
  - name: Rob Mahar
    affiliation: University of Melbourne
date: last-modified
---

# Preamble {#preamble}

```{r}
#| label: pkgs
#| code-summary: Load packages
library(tidyverse)
library(labelled)
library(kableExtra)
library(cmdstanr)
library(posterior)
library(bayestestR)
library(bayesplot)
library(matrixStats)
library(ggdist)
```

```{r}
#| label: kable-hack
#| code-summary: Hack to make kable print in dark theme
# https://stackoverflow.com/questions/53247896/the-contents-of-kableextra-table-invisible-if-rstudio-editor-theme-is-dark
print.kableExtra <- function (x, ...) {
  view_html <- getOption("kableExtra_view_html", TRUE)
  if (view_html & interactive()) {
    dep <- list(
      rmarkdown::html_dependency_jquery(), 
      rmarkdown::html_dependency_bootstrap(theme = "cosmo"), 
      kableExtra::html_dependency_kePrint(), 
      kableExtra::html_dependency_lightable()
    )
    
    x <- sub('style="', 'style="color: black; ', as.character(x), fixed = TRUE)
        
    html_kable <- htmltools::browsable(
      htmltools::HTML(
        as.character(x), 
        "<script type=\"text/x-mathjax-config\">MathJax.Hub.Config({tex2jax: {inlineMath: [[\"$\",\"$\"]]}})</script><script async src=\"https://mathjax.rstudio.com/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML\"></script>"
      )
    )
    htmltools::htmlDependencies(html_kable) <- dep
    class(html_kable) <- "shiny.tag.list"
    print(html_kable)
  }
  else {
    cat(as.character(x))
  }
}
```

```{r}

d28 <- all_dat %>% 
  filter_acs_itt() %>%
  transmute_model_cols_grp_aus_nz() %>%
  left_join(
    all_dat %>% select(StudyPatientID, starts_with("D28_EQ"), D28_death, contains("D28"), contains("DD"), contains("DIS")),
    by = "StudyPatientID")


```

# WHO 8-point outcome

## Check for discharge prior to 28 (and not dead), but WHO hospitalised on day 28

Looks like only a couple of the included data are likely to be readmissions (most are discharged at hospitalisation). Need too find out if they were truly readmitted.

```{r}

data <- d28 %>% filter(DIS_day < 28 & D28_who >= 3 & D28_death !=1)

ggplot(data, aes(x = D28_OutcomeTotalDaysHospitalised,
                 y = DIS_day)) +
  facet_wrap(~ D28_who) + 
  geom_point() + 
  geom_abline(intercept =0 , slope = 1) + theme_grey()

```

## Check for discharge on day 28, but WHO not hospitalised on day 28

Looks like only a single patient. Discharge day is the same as the total days hospitalised (both 28 days). Probably the WHO outcome is in error.  

```{r}

data <- d28 %>% filter(DIS_day == 28 & D28_who <= 3 & D28_death !=1)

```
## Check for 28 total days in hospital, but WHO not hospitalised on day 28

One of these is the same as the previous section (ALF00005). Seem like ventilated for some days, whether that helps.

```{r}

data <- d28 %>% filter(D28_OutcomeTotalDaysHospitalised == 28 & D28_who <= 3 & D28_death !=1)

```


## Check for dead but not WHO dead

None which is good. 

```{r}

data <- d28 %>% filter(D28_who !=8 & D28_death == 1)

```

# End of script.

