---
title: "Data Checks"
description: |
  Run the data checks requested by Grace.
author: "James Totterdell"
date: last-modified
format:
  docx:
    reference-doc: ../custom-reference-doc.docx
execute: 
  echo: false
  message: false
  warning: false
---

```{r}
#| label: pkgs
#| include: false
library(tidyverse)
library(kableExtra)
```

```{r}
#| label: load-data
devtools::load_all()
all_data <- read_all_no_daily()
all_daily_data <- read_all_daily()
```

## Checks

**If site has answered ‘Yes’ to needing vasopressors/inotropes at Day 28 their number of cumulative days hospitalised should be more than their number of dailies**

criteria: D28_OutcomeVasopressors == "Yes" & D28_OutcomeTotalDaysHospitalised > DIS_day where DIS_day is study day of discharge.

```{r}
all_data %>%
  filter(ENR_rec == 1, D28_OutcomeVasopressors == "Yes", D28_death != 1) %>%
  select(StudyPatientID, D28_OutcomeVasopressors, DIS_day, DD_total_days, D28_OutcomeTotalDaysHospitalised) %>%
  mutate(criteria = D28_OutcomeTotalDaysHospitalised > DIS_day) %>%
  filter(!criteria) %>%
  kable(align = "lrrrr")
```

**If site has answered ‘Yes’ to needing vasopressors/inotropes at day 28 their WHO score should be >= 6**

criteria: D28_OutcomeVasopressors == "Yes" & D28_who >= 6

```{r}
all_data %>%
  filter(ENR_rec == 1, D28_OutcomeVasopressors == "Yes") %>%
  select(StudyPatientID, D28_OutcomeVasopressors, D28_who) %>%
  mutate(criteria = D28_who >= 6) %>%
  filter(!criteria) %>%
  kable(align = "lrrrr")
```

**If site has answered WHO score =>6 at Day 28, number of days free of ventilation should be less than 28**

criteria: D28_who > 5 & D28_OutcomeDaysFreeOfVentilation < 28

```{r}
all_data %>%
  filter(ENR_rec == 1, D28_who >= 6) %>%
  select(StudyPatientID, D28_who, D28_OutcomeDaysFreeOfVentilation) %>%
  mutate(criteria = D28_OutcomeDaysFreeOfVentilation < 28) %>%
  filter(!criteria) %>%
  kable(align = "lrrrr")
```

**If site has answered WHO score 3 or above at Day 28 their number of cumulative days hospitalised should be more than their number of dailies** 

criteria: D28_who >= 3 & DIS_day < 28 & D28_OutcomeTotalDaysHospitalised > DIS_day

```{r}
all_data %>%
  filter(ENR_rec == 1, D28_who >= 3, D28_who != 8, DIS_day < 28) %>%
  select(StudyPatientID, D28_who, D28_OutcomeTotalDaysHospitalised, DIS_day, DD_total_days) %>%
  mutate(criteria = D28_OutcomeTotalDaysHospitalised > pmin(28, DIS_day))  %>%
  filter(!criteria) %>%
  kable(align = "lrrrr")
```

**Whether cumulative days hospitalised matches the number of dailies with a WHO score >= 3**

criteria: D28_OutcomeTotalDaysHospitalised >= DD_who_gteq3 where DD_who_gteq3 is number of days where WHO score was greater than or equal to 3.

```{r}
all_data %>%
 filter(ENR_rec == 1, !is.na(D28_OutcomeTotalDaysHospitalised), D28_death == 0) %>%
  select(StudyPatientID, D28_OutcomeTotalDaysHospitalised, DD_who_gteq3) %>%
  mutate(criteria = D28_OutcomeTotalDaysHospitalised >= DD_who_gteq3) %>%
  filter(!criteria) %>%
  kable(align = "lrrrr")
```

**If major bleeding or HIT occurred between discharge and Day 28, then their number of cumulative days hospitalised should be more than their number of dailies**

critera: (D28_AECHIT == "Yes" | D28_AECMajorBleeding == "Yes") & D28_OutcomeTotalDaysHospitalised > DD_total_days

```{r}
all_data %>%
 filter(ENR_rec == 1, D28_AECHIT == "Yes" | D28_AECMajorBleeding == "Yes") %>%
  select(StudyPatientID, D28_OutcomeTotalDaysHospitalised, D28_AECHIT, D28_AECMajorBleeding, DD_total_days) %>%
  mutate(criteria = D28_OutcomeTotalDaysHospitalised > DD_total_days) %>%
  filter(!criteria) %>%
  kable(align = "lrrrr")
```
