---
title: "Data Overview"
description: |
  Exploratory overview of ASCOT anticoagulation data.
author: "James Totterdell"
date: last-modified
format: 
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    captions: true
    cap-location: margin
    table-captions: true
    tbl-cap-location: margin
    reference-location: margin
    theme: journal
    fontsize: 1em
    self-contained: true
    standalone: true
    code-tools: true
    code-fold: true
    code-link: false

execute:
  warning: false
  message: false
  echo: true

engine: knitr
---

```{r}
#| label: pkgs
library(tidyverse)
library(patchwork)
library(DT)
library(plotly)
library(knitr)
library(kableExtra)

theme_set(theme_minimal(base_size = 12))

source("r/summary_functions.r")
```

```{r}
#| label: load-data
source("r/derive_full_datasets.r")
all_data <- read_all_no_daily()
all_daily_data <- read_all_daily()
```

## Dictionary

```{r}
#| label: data-dict
#| column: page
source("r/read_raw_data.r")
dict <- read_dictionary() %>%
  select(HeadingName, DbField, FieldTitle, FieldFormatting, ValidationNotes)
datatable(dict)
```

## Data Completeness

```{r}
#| label: completeness-table
#| column: page
source("r/data_completeness.r")
completeness <- summarise_completeness_data(generate_completeness_data(all_daily_data))
completeness$combined %>%
  datatable() %>%
  formatStyle(2:10, 'text-align' = "right", "white-space" = "nowrap")
```

## Available Records

```{r}
#| label: tbl-available-records
#| tbl-cap: Patterns of record availability for all screened participants.
#| cap-location: margin
all_data %>%
  count(EL_rec, ENR_rec, BAS_rec, DIS_rec, D28_rec, WTH_rec) %>%
  kable("html") %>%
  kable_styling("striped", font_size = 14)
```

## Enrolment

```{r}
#| label: fig-enrolment
#| code-summary: Study enrolment
#| fig-cap-location: margin
#| fig-cap: |
#|   Cumulative enrolments to the platform, 
#|   vertical lines indicate timing of interim analyses
md <- get_interim_dates()
id <- get_intervention_dates()
p1 <- all_data %>%
  filter(ENR_rec == 1) %>%
  count(RandDate) %>%
  complete(RandDate = seq.Date(min(RandDate), max(RandDate), by = "1 day"),
           fill = list(n = 0)) %>%
  mutate(`Cumulative enrolments` = cumsum(n)) %>%
  rename(`Randomisation date` = RandDate) %>%
  ggplot(., aes(`Randomisation date`, `Cumulative enrolments`)) +
  geom_step() +
  geom_vline(data = md,
             aes(xintercept = as.numeric(meet_date)),
             linetype = 2) +
  labs(x = "")

p2 <- id %>%
  mutate(
    CAssignment = fct_inorder(val_labels(CAssignment))
  ) %>%
  ggplot(.) +
  geom_point(aes(x = CAssignment, y = endate), shape = 4) +
  geom_segment(
    aes(x = CAssignment, xend = CAssignment, 
        y = stdate, yend = endate))  +
  geom_hline(data = md,
             aes(yintercept = as.numeric(meet_date)),
             linetype = 2) +
  coord_flip() +
  labs(x = "", y = "Calendar date")

p1 / p2
```

```{r}
#| label: fig-enrolment-country
#| code-summary: Study enrolment by country
#| fig-cap-location: margin
#| fig-cap: |
#|   Cumulative enrolments to the platform by country, 
#|   vertical lines indicate timing of interim analyses
#| fig-height: 8
p1 <- all_data %>%
  filter(ENR_rec == 1) %>%
  count(Country = PT_CountryName, RandDate) %>%
  complete(
    Country, 
    RandDate = seq.Date(min(RandDate), max(RandDate), by = "1 day"),
    fill = list(n = 0)) %>%
  group_by(Country) %>%
  mutate(`Cumulative enrolments` = cumsum(n)) %>%
  rename(`Randomisation date` = RandDate) %>%
  ggplot(., aes(`Randomisation date`, `Cumulative enrolments`)) +
  facet_wrap( ~ Country, ncol = 1, scales = "free_y") +
  geom_step() +
  geom_vline(data = md,
             aes(xintercept = as.numeric(meet_date)),
             linetype = 2) +
  labs(x = "")
(p1 / p2) + plot_layout(heights = c(4, 1))
```

```{r}
#| label: enrolment-site
#| code-summary: Study enrolment by site
#| column: screen
#| layout-nrow: 1
#| fig-align: center
#| fig-width: 20
#| fig-height: 8
p1 <- all_data %>%
  filter(ENR_rec == 1) %>%
  count(Country = PT_CountryName, Site = PT_LocationName, RandDate) %>%
  complete(
    nesting(Country, Site),
    RandDate = seq.Date(min(RandDate), max(RandDate), by = "1 day"),
    fill = list(n = 0)) %>%
  group_by(Country, Site) %>%
  mutate(`Cumulative enrolments` = cumsum(n)) %>%
  rename(`Calendar date` = RandDate) %>%
  ggplot(., aes(`Calendar date`, `Cumulative enrolments`)) +
  facet_wrap( ~ paste(Country, Site, sep = ": "), 
              ncol = 5, scales = "free_y") +
  geom_step() +
  geom_vline(data = md,
             aes(xintercept = as.numeric(meet_date)),
             linetype = 2) +
  scale_y_continuous(breaks = function(x) 
    unique(floor(pretty(seq(0, (max(x) + 1) * 1.1)))))
p1
```

## Intervention Assignments

```{r}
#| label: tbl-intervention-assignments-anticoagulation
#| tbl-cap: Counts of intervention assignments to anticoagulation
#| tbl-cap-location: margin
all_data %>%
  count(FAS_ITT, ACS_ITT, CAssignment) %>%
  kable() %>%
  kable_styling("striped", font_size = 14)
```

```{r}
#| label: tbl-intervention-assignments-both
#| tbl-cap: Counts of intervention assignments to regimen
#| tbl-cap-location: margin
all_data %>%
  count(FAS_ITT, ACS_ITT, AVS_ITT, AAssignment, CAssignment) %>%
  kable() %>%
  kable_styling("striped", font_size = 14)
```

## Baseline Factors

The following provides an overview of the baseline covariates collected for individuals.

There is an issue with the serum creatinine units for some participants. These have been reported as "umol/L" when in fact it is more likely they are in mg/dL (spike at values reported as umol/L and less than 1, noting that 1 mg/dL = 88.42 umol/L).

```{r}
#| label: fig-serum-creatinine
#| fig-cap: |
#|   Histogram of serum creatinine levels at 
#|   baseline by reported units.
all_data %>%
  filter(
    EL_SerumCreatinineUnits == "umol/L",
    EL_SerumCreatinineBlood <= 1.5
  ) %>%
  select(
    EligibilityCode, 
    StudyPatientID, 
    starts_with("EL_Serum")) %>%
  write_csv(file.path(ASCOT_DATA, "derived", "low_creatinine_values.csv"))
ggplot(all_data %>% 
         filter(!is.na(EL_SerumCreatinineUnits)), 
       aes(EL_SerumCreatinine_umolL)) +
  geom_histogram(bins = 50, boundary = 0) +
  facet_wrap( ~ EL_SerumCreatinineUnits) +
  xlim(0, 500)
```

### Demographics

```{r}
#| label: tbl-demographics-table
#| code-summary: Demographics table
#| tbl-cap: |
#|   Baseline demographics for participants randomised into
#|   the anticoagulation domain.
sdat <- all_data %>%
    filter(ENR_rec == 1, CAssignment != "C0")
generate_baseline_demographics_table(sdat, format = "html")
```

### Co-morbidities

```{r}
#| label: tbl-comorbidities-table
#| code-summary: Co-morbidities table
#| tbl-cap: |
#|   Baseline co-morbidities for participants randomised into
#|   then anticoagulation domain.
sdat <- all_data %>%
    filter(ENR_rec == 1, CAssignment != "C0")
generate_baseline_comorbidities_table(sdat, format = "html")
```

### Prognostics

```{r}
#| label: tbl-prognostics-table
#| code-summary: Prognostics table
#| tbl-cap: |
#|   Baseline prognostic variables for 
#|   participants randomised into anticoagulation domain.
sdat <- all_data %>%
    filter(ENR_rec == 1, CAssignment != "C0")
generate_baseline_prognostics_table(sdat, format = "html")
```
