---
title: "7-2 WHO 8-point Outcome Scale"
description: |
  Working analyses of the WHO 8-point outcome scale outcome.
author:
  - name: James Totterdell
    affiliation: University of Sydney
  - name: Rob Mahar
    affiliation: University of Melbourne
date: today
toc-depth: 5
---

# Preamble {#preamble}

```{r}
#| label: pkgs
#| code-summary: Load packages
library(tidyverse)
library(labelled)
library(kableExtra)
library(cmdstanr)
library(posterior)
library(bayestestR)
library(bayesplot)
library(matrixStats)
library(ggdist)
library(patchwork)
library(lubridate)

theme_set(theme_classic(base_size = 10, base_family = "Palatino") +
  theme(panel.grid = element_blank(),
        strip.background = element_blank()))
bayesplot_theme_set(theme_set(theme_classic(base_size = 10, base_family = "Palatino") +
  theme(panel.grid = element_blank(),
        strip.background = element_blank())))
```

```{r}
logit <- function(x) log(x) - log(1 - x)
expit <- function(x) 1 / (1 + exp(-x))
ordered_logit <- function(x) {
  c(
    1 - expit(-x[1]),
    expit(-x[1:(length(x)-1)]) - expit(-x[2:(length(x))]),
    expit(-tail(x, 1))
  )
}
```

```{r}
#| label: data
#| code-summary: Prepare dataset
devtools::load_all()
all_dat <- read_all_no_daily()

acs_itt_dat <- all_dat %>% 
  filter_acs_itt() %>%
  transmute_model_cols_grp_aus_nz()
acs_itt_nona_dat <- acs_itt_dat %>%
  filter(!is.na(D28_who))

# Concurrent enrolments for C2
acs_itt_concurc2_dat <- acs_itt_dat %>%
  filter_concurrent_intermediate()
acs_itt_concurc2_nona_dat <- acs_itt_concurc2_dat %>% 
  filter(!is.na(D28_who))

# Concurrent enrolments for C3
acs_itt_concurc3_dat <- acs_itt_dat %>%
  filter_concurrent_std_aspirin()
acs_itt_concurc3_nona_dat <- acs_itt_concurc3_dat %>% 
  filter(!is.na(D28_who))

# Concurrent enrolments for C4
acs_itt_concurc4_dat <- acs_itt_dat %>%
  filter_concurrent_therapeutic()
acs_itt_concurc4_nona_dat <- acs_itt_concurc4_dat %>% 
  filter(!is.na(D28_who))
```

```{r}
#| label: models
#| code-summary: Load models
ordmod0 <- cmdstan_model(
  "stan/ordinal/logistic_cumulative.stan") # No epoch or site
ordmod_epoch <- cmdstan_model(
  "stan/ordinal/logistic_cumulative_epoch.stan") # Epoch only
ordmod <- cmdstan_model(
  "stan/ordinal/logistic_cumulative_epoch_site.stan") # Full model
logistic <- cmdstan_model(file.path("stan", "binary", "logistic_site_epoch.stan"))
```

```{r}
#| label: helpers
#| code-summary: Helper functions
make_summary_table <- function(dat, format = "html") {
  tdat <- dat %>%
  group_by(CAssignment = factor(CAssignment, 
                                levels = c("C1", "C2", "C3", "C4"),
                                labels = intervention_labels2()$CAssignment[-1])) %>%
  summarise(
    Patients = n(),
    Known = sum(!is.na(D28_who)),
    Deaths = sprintf("%i (%.0f%%)", 
                     sum(D28_who == 8, na.rm = TRUE), 
                     100 * mean(D28_who == 8, na.rm = TRUE)),
    `Hospitalised` = sprintf("%i (%.0f%%)", 
                     sum(D28_who > 2 & D28_who < 8, na.rm = TRUE), 
                     100 * mean(D28_who > 2 & D28_who < 8, na.rm = TRUE)),
    `WHO, Median (Q1, Q3)` = sprintf(
      "%.0f (%.0f, %.0f)", 
      median(D28_who, na.rm = T), 
      quantile(D28_who, 0.25, na.rm = TRUE), 
      quantile(D28_who, 0.75, na.rm = TRUE))
  ) %>%
  bind_rows(
    dat %>%
  group_by(CAssignment = "Overall") %>%
  summarise(
    Patients = n(),
    Known = sum(!is.na(D28_who)),
    Deaths = sprintf("%i (%.0f%%)", 
                     sum(D28_who == 8, na.rm = TRUE), 
                     100 * mean(D28_who == 8, na.rm = TRUE)),
    `Hospitalised` = sprintf("%i (%.0f%%)", 
                     sum(D28_who > 2 & D28_who < 8, na.rm = TRUE), 
                     100 * mean(D28_who > 2 & D28_who < 8, na.rm = TRUE)),
    `WHO, Median (Q1, Q3)` = sprintf(
      "%.0f (%.0f, %.0f)", 
      median(D28_who, na.rm = T), 
      quantile(D28_who, 0.25, na.rm = TRUE), 
      quantile(D28_who, 0.75, na.rm = TRUE))
  )
  ) %>%
  rename(`Anticoagulation\nintervention` = CAssignment)
  kable(
    tdat,
    format = format,
    align = "lrrrrr",
    booktabs = TRUE,
    linesep = ""
  ) %>%
    kable_styling(
      font_size = 9,
      latex_options = "HOLD_position"
    ) %>%
    row_spec(nrow(tdat), bold = T)
}

make_primary_model_data <- function(
    dat, 
    vars = NULL,
    beta_sd_var = NULL,
    ctr = contr.orthonorm,
    outcome = "D28_who",
    p_mult = 2) {
  
  X <- make_X_design(dat, vars, ctr)
  attX <- attr(X, "contrasts")
  X <- X[, -1]
  attr(X, "contrasts") <- attX
  nXtrt <- sum(grepl("rand", colnames(X)))
  
  beta_sd <- c(rep(1, nXtrt), beta_sd_var)
  
  epoch <- dat$epoch
  M_epoch <- max(dat$epoch)
  region <- dat$ctry_num
  M_region <- max(region)
  site <- dat$site_num
  M_site <- max(site)
  region_by_site <- dat %>% 
    dplyr::count(ctry_num, site_num) %>% 
    pull(ctry_num)

  y_raw <- ordered(dat[[outcome]])
  y_mod <- as.integer(y_raw)
  N <- dim(X)[1]
  K <- dim(X)[2]
  unique_y <- length(unique(y_mod))
  list(N = N, K = K, J = unique_y, X = X, 
       y = y_mod, y_raw = y_raw,
       M_region = M_region,
       M_site = M_site, site = site,
       M_epoch = M_epoch, epoch = epoch,
       region_by_site = region_by_site,
       p_par = p_mult * rep(1 / unique_y, unique_y),
       beta_sd = beta_sd)  
}
```


# Descriptive {#descriptive}

## Anticoagulation

```{r}
#| label: tbl-7-2-summary
#| code-summary: Summary of WHO outcome by arm
#| tbl-cap: Summary of WHO scale at day 28 by treatment group.
save_tex_table(
  make_summary_table(acs_itt_dat, "latex"), 
  file.path("outcomes", "secondary", "7-2-anticoagulation-summary"))
make_summary_table(acs_itt_dat)
```

```{r}
p <- acs_itt_nona_dat %>%
  dplyr::count(
    CAssignment = factor(
      CAssignment, 
      labels = str_replace(intervention_labels()$CAssignment[-1], "<br>", "\n")), 
    D28_who = ordered(as.integer(D28_who), levels = 1:8)
  ) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n)) %>%
  ggplot(., aes(CAssignment, p)) +
  geom_col(aes(fill = D28_who)) +
  scale_fill_viridis_d(option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = F)) +
  labs(fill = "WHO scale", y = "Cumulative proportion", x = "Anticoagulation intervention")
pth <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(pth, "outcome-7-2-descriptive.pdf"), p, height = 3, width = 6)
p
```

```{r}
acs_itt_nona_dat %>%
  dplyr::count(CAssignment, D28_who = factor(as.integer(D28_who))) %>%
  complete(CAssignment, D28_who, fill = list(n = 0)) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n)) %>%
  ggplot(., aes(D28_who, p)) +
  facet_wrap( ~ CAssignment) +
  geom_point() +
  geom_segment(aes(xend = D28_who, y = 0, yend = p))
```

## Age

```{r}
#| label: fig-7-2-age
#| fig-cap: |
#|   Distribution of WHO scale at day 28 by age group
#| fig-height: 4
pdat <- all_dat %>%
  filter_acs_itt() %>%
  filter(!is.na(D28_who)) %>%
  dplyr::count(
    agegrp = cut(AgeAtEntry, c(18, seq(25, 75, 5), 100), include.lowest = T, right = F),
    who = ordered(D28_who, levels = 1:8), 
    .drop = F) %>%
  group_by(agegrp) %>%
  mutate(p = n / sum(n))
pdat2 <- pdat %>%
  group_by(agegrp) %>%
  summarise(n = sum(n))

p1 <- ggplot(pdat2, aes(agegrp, n)) +
  geom_col(colour = "grey40", fill = "grey40") +
  geom_vline(xintercept = 60, linetype = 2) +
  labs(y = "Number of\nparticipants",
       x = "Age at entry") +
  geom_vline(xintercept = 8.5, linetype = 2) +
  theme(axis.text.x = element_text(hjust = 1, angle = 45))

p2 <- ggplot(pdat, aes(agegrp, p)) +
  geom_col(aes(fill = who)) +
  labs(x = "Age", y = "Cumulative\nproportion") +
  scale_fill_viridis_d("WHO scale", option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = F)) +
  geom_vline(xintercept = 8.5, linetype = 2) +
  theme(axis.text.x = element_text(hjust = 1, angle = 45)) +
  theme(legend.key.size = unit(0.5, "lines"))
p <- p1 | p2
path <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(path, "7-2-age.pdf"), p, height = 2.5, width = 6)
p
```

## Country

```{r}
#| label: fig-7-2-country
#| fig-cap: |
#|   Distribution of WHO scale at day 28 by country.
#| fig-height: 4
pdat <- all_dat %>%
  filter_acs_itt() %>%
  filter(!is.na(D28_who)) %>%
  dplyr::count(
    Country = factor(PT_CountryName, levels = c("India", "Australia", "Nepal", "New Zealand"),
                     labels = c("India", "Australia", "Nepal", "New\nZealand")),
    who = ordered(D28_who, levels = 1:8), 
    .drop = F) %>%
  group_by(Country) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup()
pdat2 <- pdat %>%
  group_by(Country) %>%
  summarise(n = sum(n))

p1 <- ggplot(pdat2, aes(Country, n)) +
  geom_col() +
    labs(
      y = "Number of\nparticipants", 
      x = "Country of enrolment")

p2 <- ggplot(pdat, aes(Country, p)) +
  geom_col(aes(fill = who)) +
  labs(x = "Anticoagulation intervention", y = "Cumulative\nproportion") +
  scale_fill_viridis_d("WHO scale", option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = F)) +
  theme(legend.key.size = unit(0.5, "lines"))
p <- p1 | p2
path <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(path, "7-2-country.pdf"), p, height = 2.5, width = 6)
p
```

## Site

```{r}
#| label: fig-7-2-site
#| fig-cap: |
#|   Distribution of WHO scale by study site
#| fig-height: 4
pdat <- all_dat %>%
  filter_acs_itt() %>%
  filter(!is.na(D28_who)) %>%
  dplyr::count(
    Country = factor(PT_CountryName, levels = c("India", "Australia", "Nepal", "New Zealand"),
                     labels = c("India", "Australia", "Nepal", "New\nZealand")),
    Site = fct_infreq(Location),
    who = ordered(D28_who, levels = 1:8)) %>%
  complete(who = ordered(1:8), nesting(Country, Site), fill = list(n = 0)) %>%
  group_by(Country, Site) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup() %>%
  mutate(
    Country = droplevels(Country),
    Site = droplevels(Site)
  )
pdat2 <- pdat %>%
  group_by(Country, Site) %>%
  summarise(n = sum(n)) %>%
  ungroup()
p1 <- ggplot(pdat2, aes(Site, n)) +
  facet_grid( ~ Country, scales = "free_x", space = "free_x") +
  geom_col() +
    labs(
      y = "Number of\nparticipants", 
      x = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.border = element_rect(fill = NA))
p2 <- ggplot(pdat, aes(Site, p)) +
  facet_grid( ~ Country, scales = "free_x", space = "free_x") +
  geom_col(aes(fill = who)) +
  labs(x = "Anticoagulation intervention", y = "Cumulative\nproportion") +
  scale_fill_viridis_d("WHO scale", option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = F, ncol = 1)) +
  theme(axis.text.x = element_text(hjust = 1, angle = 45)) +
  theme(legend.key.size = unit(0.25, "lines"))
p <- p1 / p2 +
  plot_layout(guides = 'collect')
path <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(path, "7-2-country-site.pdf"), p, height = 4, width = 6.25)
p
```

## Calendar Time

```{r}
#| label: fig-7-2-calendar
#| fig-cap: |
#|   Distribution of WHO scale by calendar time.
#| fig-height: 4
pdat <- acs_itt_nona_dat %>%
  dplyr::count(
    yr = year(RandDate), mth = month(RandDate),
    who = ordered(D28_who, levels = 1:8), 
    .drop = F) %>%
  group_by(yr, mth) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup()
p1 <- pdat %>%
  group_by(yr, mth) %>%
  summarise(n = sum(n)) %>%
  ggplot(., aes(mth, n))  +
  facet_grid( ~ yr, drop = T, scales = "free_x", space = "free") +
    geom_col() +
    labs(
      y = "Number of\nparticipants", 
      x = "Calendar date (month of year)") +
  scale_x_continuous(breaks = 1:12)
p2 <- ggplot(pdat, aes(mth, p)) +
  facet_grid( ~ yr, drop = T, scales = "free_x", space = "free") +
  geom_col(aes(fill = who)) +
  labs(x = "Calendar date (month of year)", y = "Cumulative\nproportion") +
  scale_fill_viridis_d("WHO scale", option = "A", direction = -1) +
  guides(fill = guide_legend(reverse = F)) +
  theme(legend.key.size = unit(0.5, "lines")) +
  scale_x_continuous(breaks = 1:12)
p <- p1 | p2
path <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(path, "7-2-calendar-time.pdf"), p, height = 2, width = 6)
p
```

## Sample Cumulative Logits

Proportional odds looks reasonable for all logits except 1.

```{r}
#| code-summary: Plot sample cumulative logits
#| fig-cap: Inspect sample cumulative logits.
trt_counts <- acs_itt_nona_dat %>%
  dplyr::count(CAssignment, D28_who) %>%
  complete(CAssignment, D28_who, fill = list(n = 0)) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n))
trt_logit <- trt_counts %>% 
  group_by(CAssignment) %>% 
  mutate(clogit = logit(cumsum(p))) %>%
  group_by(D28_who) %>%
  mutate(rel_clogit = clogit - mean(clogit)) %>%
  filter(D28_who != 28)

ggplot(trt_logit, aes(CAssignment, rel_clogit)) +
  facet_wrap( ~ D28_who) +
  geom_point() +
  labs(y = "Relative (to mean) sample cumulative logit")

ggplot(trt_logit, aes(D28_who, rel_clogit)) +
  facet_wrap( ~ CAssignment) +
  geom_point() +
  labs(y = "Relative (to mean) sample cumulative logit")
```

# Modelling {#modelling}

## Primary Model

```{r}
#| label: fit-model-primary
#| code-summary: Fit primary model
fit_primary_model <- function(dat, ctr = contr.orthonorm, save = FALSE) {
  mdat <- make_primary_model_data(
    dat, c("inelgc3", "agegte60", "ctry"), 
    c(10, 2.5, 1, 1), 
    ctr)
  snk <- capture.output(
    mfit <- ordmod$sample(
      data = mdat,
      seed = 712508,
      chains = 8,
      parallel_chains = 8,
      iter_warmup = 1000,
      iter_sampling = 2500,
      refresh = 0,
      adapt_delta = 0.98
  ))
  if (save) {
    mfit$save_object(file.path("outputs", "models", "secondary", "7-2.rds"))  
  }
  mdrws <- as_draws_rvars(mfit$draws())
  # Add names
  epoch_map <- dat %>% dplyr::count(epoch, epoch_lab)
  site_map <- dat %>% dplyr::count(site_num, site)
  names(mdrws$beta) <- colnames(mdat$X)
  names(mdrws$gamma_epoch) <- epoch_map$epoch_lab
  names(mdrws$gamma_site) <- site_map$site
  # Convert to treatment log odds ratios
  mdrws$Acon <- attr(mdat$X, "contrasts")$randA %**% mdrws$beta[grepl("randA[0-9]", names(mdrws$beta))]
  mdrws$Ccon <- attr(mdat$X, "contrasts")$randC %**% mdrws$beta[grepl("randC[0-9]", names(mdrws$beta))]
  mdrws$trtA <- mdrws$Acon[-1] - mdrws$Acon[1]
  mdrws$trtC <- mdrws$Ccon[-1] - mdrws$Ccon[1]
  mdrws$compare <- c(
    "Intermediate vs low" = exp(mdrws$trtC[1]),
    "Low with aspirin vs low" = exp(mdrws$trtC[2]),
    "Therapeutic vs low" = exp(mdrws$trtC[3]),
    "Intermediate vs low with aspirin" = exp(mdrws$trtC[1] - mdrws$trtC[2]),
    "Intermediate vs therapeutic" = exp(mdrws$trtC[1] - mdrws$trtC[3]),
    "Low with aspirin vs therapeutic" = exp(mdrws$trtC[2] - mdrws$trtC[3])
  )
  mdrws$OR <- c(
    setNames(exp(mdrws$trtC), 
             c("Intermediate", "Low with aspirin", "Therapeutic")),
    "Ineligible aspirin" = exp(mdrws$beta[which(grepl("inelg", colnames(mdat$X)))]),
    "Age \u2265 60" = exp(mdrws$beta[which(grepl("age", colnames(mdat$X)))]),
    setNames(exp(mdrws$beta[which(grepl("ctry", colnames(mdat$X)))]), 
             c("Australia/New Zealand", "Nepal"))
  )
  return(list(dat = mdat, fit = mfit, drws = mdrws))
}
res <- fit_primary_model(acs_itt_nona_dat, save = TRUE)
```

```{r}
#| label: odds-ratio-summary-table-primary-model-save
#| code-summary: Odds ratio summary table
#| tbl-cap: Posterior summaries for model parameters (fixed-effects).
save_tex_table(
  odds_ratio_summary_table(res$drws$OR, "latex"),
  "outcomes/secondary/7-2-primary-model-acs-itt-summary-table")
odds_ratio_summary_table(res$drws$OR)
```

```{r}
#| code-summary: Odds ratio summary for epoch and site
#| fig-cap: Summary of epoch and site posterior odds ratios.
p <- plot_epoch_site_terms(
  exp(res$drws$gamma_epoch),
  exp(res$drws$gamma_site),
  factor(res$dat$region_by_site, 
         labels = c("India", "Australia\nNew Zealand", "Nepal"))
)
pth <- file.path("outputs", "figures", "outcomes", "secondary", "7-2-primary-model-epoch-site-terms.pdf")
ggsave(pth, p, width = 6, height = 4.5)
p
```

```{r}
#| fig-cap: Posterior densities for treatment comparisons.
p <- plot_or_densities(res$drws$compare)
p
```

:::{.callout-caution collapse="true"}
### Diagnostics
```{r}
res$fit$summary()
res$fit$diagnostic_summary()
```
:::

:::{.callout-caution collapse="true"}
### Trace plots
```{r}
mcmc_trace(res$drws["beta"])
mcmc_trace(res$drws["alpha"])
mcmc_trace(res$drws["gamma_site"])
mcmc_trace(res$drws["gamma_epoch"])
```
:::

### Posterior Predictive

```{r}
y_ppc <- res$drws$y_ppc
ppc_dat <- bind_cols(acs_itt_nona_dat, tibble(y_ppc = y_ppc))

grp_ppc1 <- function(grp) {
  ppc_dat  %>%
  group_by(grp = !!grp) %>%
  summarise(
    y_1 = mean(D28_who == 1),
    ypp_1 = rvar_mean(y_ppc == 1),
    y_2 = mean(D28_who <= 2),
    ypp_2 = rvar_mean(y_ppc <= 2),
    y_3 = mean(D28_who <= 3),
    ypp_3 = rvar_mean(y_ppc <= 3),
    y_4 = mean(D28_who <= 4),
    ypp_4 = rvar_mean(y_ppc <= 4),
    y_5 = mean(D28_who <= 5),
    ypp_5 = rvar_mean(y_ppc <= 5),
    y_6 = mean(D28_who <= 6),
    ypp_6 = rvar_mean(y_ppc <= 6),
    y_7 = mean(D28_who <= 7),
    ypp_7 = rvar_mean(y_ppc <= 7),
    y_8 = mean(D28_who <= 8),
    ypp_8 = rvar_mean(y_ppc <= 8)
  ) %>%
  pivot_longer(y_1:ypp_8, names_to = c("response", "who"), names_sep = "_", values_to = "posterior") %>%
  mutate(who = as.numeric(who))
}

grp_ppc2 <- function(grp) {
  ppc_dat  %>%
  group_by(grp = !!grp) %>%
  summarise(
    y_1 = mean(D28_who == 1),
    ypp_1 = rvar_mean(y_ppc == 1),
    y_2 = mean(D28_who == 2),
    ypp_2 = rvar_mean(y_ppc == 2),
    y_3 = mean(D28_who == 3),
    ypp_3 = rvar_mean(y_ppc == 3),
    y_4 = mean(D28_who == 4),
    ypp_4 = rvar_mean(y_ppc == 4),
    y_5 = mean(D28_who == 5),
    ypp_5 = rvar_mean(y_ppc == 5),
    y_6 = mean(D28_who == 6),
    ypp_6 = rvar_mean(y_ppc == 6),
    y_7 = mean(D28_who == 7),
    ypp_7 = rvar_mean(y_ppc == 7),
    y_8 = mean(D28_who == 8),
    ypp_8 = rvar_mean(y_ppc == 8)
  ) %>%
  pivot_longer(y_1:ypp_8, names_to = c("response", "who"), 
               names_sep = "_", values_to = "posterior") %>%
  mutate(who = as.numeric(who))
}

plot_grp_ppc <- function(dat) {
  ggplot(dat %>% filter(response == "ypp"), aes(x = who)) +
    facet_wrap( ~ grp, nrow = 1) +
    stat_slabinterval(aes(ydist = posterior))  +
    geom_point(data = dat %>% filter(response == "y"), 
               aes(x = who, y = mean(posterior)),
               colour = "red",
               shape = 23) +
    labs(x = "WHO outcome", 
         y = "Probability")
}

plot_grp_ppc <- function(dat, lab = "", xlab = "Probability") {
  ggplot(dat %>% filter(response == "ypp"), aes(y = who)) +
    facet_wrap( ~ grp, nrow = 1) +
    stat_slabinterval(aes(xdist = posterior), fatten_point = 1)  +
    geom_point(data = dat %>% filter(response == "y"), 
               aes(y = who, x = mean(posterior)),
               colour = "red",
               shape = 23) +
    scale_x_continuous(xlab, breaks = c(0, 0.5),
                       sec.axis = sec_axis(~ . , name = lab, breaks = NULL, labels = NULL)) +
    scale_y_continuous("WHO\noutcome", breaks = c(1,3,5,7)) +
    theme(strip.text = element_text(size = rel(0.7)),
          axis.title.x = element_text(size = rel(0.7)),
          axis.text.x = element_text(size = rel(0.65)),
          axis.title.y = element_text(size = rel(0.75)),
          axis.title.x.bottom = element_blank())
}

pp_epoch <- grp_ppc2(sym("epoch")) %>% 
  mutate(grp = fct_inorder(factor(grp)))
pp_C <- grp_ppc2(sym("CAssignment"))
pp_ctry <- grp_ppc2(sym("country"))
pp_site <- grp_ppc2(sym("site")) %>%
  left_join(ppc_dat %>% dplyr::count(site, country), by = c("grp" = "site"))

p1 <- plot_grp_ppc(pp_C, "Anticoagulation", "")
p2 <- plot_grp_ppc(pp_ctry, "Country", "") 
p3 <- plot_grp_ppc(pp_epoch, "Epoch", "")
p4 <- plot_grp_ppc(pp_site %>% filter(country == "IN"), "Sites India", "")
p5 <- plot_grp_ppc(pp_site %>% filter(country == "AU"), "Sites Australia", "")
p6 <- plot_grp_ppc(pp_site %>% filter(country == "NP"), "Sites Nepal", "")
p7 <- plot_grp_ppc(pp_site %>% filter(country == "NP"), "Sites New Zealand", "")
p <- (p1 | p2) / p3 / p4 / p5 / (p6 | p7)
pth <- file.path("outputs", "figures", "outcomes", "secondary",
                 "7-2-primary-model-acs-itt-ppc.pdf")
ggsave(pth, p, width = 6, height = 5.75)
p
```


## Sensitivity: Concurrent controls

### Intermediate dose

- **Set**: ACS-ITT-intermediate
- **Covariates**: anticoagulation intervention, age group, region of enrolment.

```{r}
#| code-summary: Descriptive summary table
save_tex_table(
  make_summary_table(acs_itt_concurc2_dat, "latex"), 
  file.path("outcomes", "secondary", "7-2-anticoagulation-concurrent-intermediate-summary"))
make_summary_table(acs_itt_concurc2_dat)
```

```{r}
#| code-summary: Sample distribution
#| fig-cap: |
#|   Distribution of WHO outcome scale, ACS-ITT-intermediate.
#| fig-height: 4
pdat <- acs_itt_concurc2_nona_dat %>%
  dplyr::count(
    CAssignment = factor(
      CAssignment, 
      levels = c("C1", "C2"),
      labels = c("Low", "Intermediate")),
    who = ordered(D28_who, levels = 1:8), 
    .drop = F) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup()
p <- ggplot(pdat, aes(CAssignment, p)) +
  geom_col(aes(fill = who), colour = NA) +
  labs(x = "Anticoagulation intervention", y = "Cumulative proportion") +
  scale_fill_viridis_d("WHO scale", option = "A", direction = -1) +
  theme(legend.key.size = unit(0.75, "lines"))
pth <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(pth, "outcome-7-2-descriptive-concurrent-intermediate.pdf"), p, height = 2.5, width = 4)
p
```

```{r}
#| code-summary: Fit model
ctr <- contr.orthonorm
X <- model.matrix( 
  ~ CAssignment + agegte60 + ctry, 
  data = acs_itt_concurc2_nona_dat, 
  contrasts.arg = list(CAssignment = ctr))[, -1]
y_raw <- ordered(acs_itt_concurc2_nona_dat$D28_who)
y_mod <- as.integer(y_raw)
N <- dim(X)[1]
K <- dim(X)[2]
unique_y <- length(unique(y_mod))
mdat <- list(
  N = N, K = K, J = unique_y, X = X, y = y_mod, y_raw = y_raw,
  p_par = 2 * rep(1 / unique_y, unique_y),
  beta_sd = c(1, 2.5, 1, 1)
)
snk <- capture.output(
  mfit <- ordmod0$sample(
    data = mdat,
    seed = 75136,
    chains = 8,
    parallel_chains = 8,
    iter_warmup = 1000,
    iter_sampling = 2500,
    refresh = 0
))
mdrws <- as_draws_rvars(mfit$draws())
names(mdrws$beta) <- colnames(X)
mdrws$Ccon <- as.vector(ctr(2) %**% mdrws$beta[1])
mdrws$Ctrt <- mdrws$Ccon[-1] - mdrws$Ccon[1]
mdrws$compare <- c("Intermediate vs low" = exp(mdrws$Ctrt[1]))
mdrws$OR <- c("Intermediate" = exp(mdrws$Ctrt), 
              setNames(exp(mdrws$beta[2:4]), c("Age \u2265 60", "Australia/New Zealand", "Nepal")))
```

```{r}
#| code-summary: Posterior contrast
#| tbl-cap: Posterior densities for comparisons of interest.
p <- plot_or_densities(mdrws$compare)
p
```

```{r}
#| code-summary: Odds ratio summary table
#| tbl-cap: Posterior summaries for model parameters.
save_tex_table(
  odds_ratio_summary_table(mdrws$OR, "latex"),
  "outcomes/secondary/7-2-primary-model-acs-itt-concurrent-intermediate-summary-table")
odds_ratio_summary_table(mdrws$OR)
```

:::{.callout-caution collapse="true"}
#### Diagnostics
```{r}
mfit$summary()
mfit$diagnostic_summary()
```
:::

:::{.callout-caution collapse="true"}
#### Trace plots
```{r}
mcmc_trace(mdrws["beta"])
mcmc_trace(mdrws["alpha"])
```
:::


### Low-dose with aspirin

- **Set**: ACS-ITT-aspirin
- **Covariates**: anticoagulation intervention, age group, region of enrolment.

```{r}
#| code-summary: Descriptive summary table
save_tex_table(
  make_summary_table(acs_itt_concurc3_dat, "latex"), 
  file.path("outcomes", "secondary", "7-2-anticoagulation-concurrent-stdaspirin-summary"))
make_summary_table(acs_itt_concurc3_dat)
```

```{r}
#| code-summary: Sample distribution
#| fig-cap: |
#|   Distribution WHO outcome scale, ACS-ITT-aspirin.
#| fig-height: 4
pdat <- acs_itt_concurc3_nona_dat %>%
  dplyr::count(
    CAssignment = factor(
      CAssignment, 
      levels = c("C1", "C2", "C3"),
      labels = c("Low", "Intermediate", "Low\nwith aspirin")),
    who = ordered(D28_who, levels = 1:8), 
    .drop = F) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup()
p <- ggplot(pdat, aes(CAssignment, p)) +
  geom_col(aes(fill = who)) +
  labs(x = "Anticoagulation intervention", y = "Cumulative proportion") +
  scale_fill_viridis_d("WHO scale", option = "A", direction = -1) +
  theme(legend.key.size = unit(0.75, "lines"))
pth <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(pth, "outcome-7-2-descriptive-concurrent-stdaspirin.pdf"), p, height = 2.5, width = 6)
p
```

```{r}
#| code-summary: Fit model
ctr <- contr.orthonorm
X <- model.matrix( 
  ~ CAssignment + agegte60 + ctry, 
  data = acs_itt_concurc3_nona_dat, 
  contrasts.arg = list(CAssignment = ctr))[, -1]
y_raw <- ordered(acs_itt_concurc3_nona_dat$D28_who)
y_mod <- as.integer(y_raw)
N <- dim(X)[1]
K <- dim(X)[2]
unique_y <- length(unique(y_mod))
mdat <- list(
  N = N, K = K, J = unique_y, X = X, y = y_mod, y_raw = y_raw,
  p_par = 2 * rep(1 / unique_y, unique_y),
  beta_sd = c(1, 1, 2.5, 1)
)
snk <- capture.output(
  mfit <- ordmod0$sample(
    data = mdat,
    seed = 135356,
    chains = 8,
    parallel_chains = 8,
    iter_warmup = 1000,
    iter_sampling = 2500,
    refresh = 0
))
mdrws <- as_draws_rvars(mfit$draws())
names(mdrws$beta) <- colnames(X)
mdrws$Ccon <- as.vector(ctr(3) %**% mdrws$beta[1:2])
mdrws$Ctrt <- mdrws$Ccon[-1] - mdrws$Ccon[1]
mdrws$compare <- c("Intermediate vs low" = exp(mdrws$Ctrt[1]),
                   "Low with aspirin vs low" = exp(mdrws$Ctrt[2]),
                   "Intermediate vs low with aspirin" = exp(mdrws$Ctrt[1] - mdrws$Ctrt[2]))
mdrws$OR <- c("Intermediate" = exp(mdrws$Ctrt[1]),
              "Low with aspirin" = exp(mdrws$Ctrt[2]),
              setNames(exp(mdrws$beta[3:4]), c("Age \u2265 60", "Australia/New Zealand")))
```

```{r}
#| code-summary: Posterior contrast
#| tbl-cap: Decision summaries on comparisons
plot_or_densities(mdrws$compare)
```

```{r}
#| code-summary: Odds ratio summary table
#| tbl-cap: Posterior summaries for model parameters.
save_tex_table(
  odds_ratio_summary_table(mdrws$OR, "latex"),
  "outcomes/secondary/7-2-primary-model-acs-itt-concurrent-stdaspirin-summary-table")
odds_ratio_summary_table(mdrws$OR)
```

:::{.callout-caution collapse="true"}
#### Diagnostics
```{r}
mfit$summary()
mfit$diagnostic_summary()
```
:::

:::{.callout-caution collapse="true"}
#### Trace plots
```{r}
mcmc_trace(mdrws["beta"])
mcmc_trace(mdrws["alpha"])
```
:::

### Therapeutic dose

- **Set**: ACS-ITT-therapeutic
- **Covariates**: anticoagulation intervention, age group, region of enrolment.

```{r}
#| code-summary: Descriptive summary table
save_tex_table(
  make_summary_table(acs_itt_concurc4_dat, "latex"), 
  file.path("outcomes", "secondary", "7-2-anticoagulation-concurrent-therapeutic-summary"))
make_summary_table(acs_itt_concurc4_dat)
```

```{r}
#| code-summary: Sample distribution
#| fig-cap: |
#|   Distribution of WHO outcome scale, ACS-ITT-therapeutic.
#| fig-height: 4
pdat <- acs_itt_concurc4_nona_dat %>%
  dplyr::count(
    CAssignment = factor(
      CAssignment, 
      levels = c("C1", "C2", "C4"),
      labels = c("Low", "Intermediate", "Therapeutic")),
    who = ordered(D28_who, levels = 1:8), 
    .drop = F) %>%
  group_by(CAssignment) %>%
  mutate(p = n / sum(n)) %>%
  mutate(cp = cumsum(p)) %>%
  ungroup()
p <- ggplot(pdat, aes(CAssignment, p)) +
  geom_col(aes(fill = who)) +
  labs(x = "Anticoagulation intervention", y = "Cumulative proportion") +
  scale_fill_viridis_d("WHO scale", option = "A", direction = -1) +
  theme(legend.key.size = unit(0.75, "lines"))
pth <- file.path("outputs", "figures", "outcomes", "secondary")
ggsave(file.path(pth, "outcome-7-2-descriptive-concurrent-therapeutic.pdf"), p, height = 2.5, width = 6)
p
```

```{r}
#| code-summary: Fit model
ctr <- contr.orthonorm
X <- model.matrix( 
  ~ CAssignment + agegte60 + ctry, 
  data = acs_itt_concurc4_nona_dat, 
  contrasts.arg = list(CAssignment = ctr))[, -1]
y_raw <- ordered(acs_itt_concurc4_nona_dat$D28_who)
y_mod <- as.integer(y_raw)
N <- dim(X)[1]
K <- dim(X)[2]
unique_y <- length(unique(y_mod))
mdat <- list(
  N = N, K = K, J = unique_y, X = X, y = y_mod, y_raw = y_raw,
  p_par = 2 * rep(1 / unique_y, unique_y),
  beta_sd = c(1, 1, 2.5, 1, 1)
)

snk <- capture.output(
  mfit <- ordmod0$sample(
    data = mdat,
    seed = 49135,
    chains = 8,
    parallel_chains = 8,
    iter_warmup = 1000,
    iter_sampling = 2500,
    refresh = 0
))
mdrws <- as_draws_rvars(mfit$draws())
names(mdrws$beta) <- colnames(X)
mdrws$Ccon <- as.vector(ctr(3) %**% mdrws$beta[1:2])
mdrws$Ctrt <- mdrws$Ccon[-1] - mdrws$Ccon[1]
mdrws$compare <- c("Intermediate vs low" = exp(mdrws$Ctrt[1]),
                   "Therapeutic vs low" = exp(mdrws$Ctrt[2]),
                   "Intermediate vs therapeutic" = exp(mdrws$Ctrt[1] - mdrws$Ctrt[2]))
mdrws$OR <- c("Intermediate" = exp(mdrws$Ctrt[1]),
              "Therapeutic" = exp(mdrws$Ctrt[2]),
              setNames(exp(mdrws$beta[3:5]), c("Age \u2265 60", "India", "Australia/New Zealand")))
```

```{r}
#| code-summary: Posterior contrasts
#| tbl-cap: Decision summaries on comparisons
plot_or_densities(mdrws$compare)
```

```{r}
#| code-summary: Odds ratio summary table
#| tbl-cap: Posterior summaries for model parameters.
save_tex_table(
  odds_ratio_summary_table(mdrws$OR, "latex"),
  "outcomes/secondary/7-2-primary-model-acs-itt-concurrent-therapeutic-summary-table")
odds_ratio_summary_table(mdrws$OR)
```

:::{.callout-caution collapse="true"}
#### Diagnostics
```{r}
mfit$summary()
mfit$diagnostic_summary()
```
:::

:::{.callout-caution collapse="true"}
#### Trace plots
```{r}
mcmc_trace(mdrws["beta"])
mcmc_trace(mdrws["alpha"])
```
:::

## Sensitivity: Treatment contrast prior

```{r}
#| label: fit-model-primary-trt-ctr
#| code-summary: Fit primary model
res <- fit_primary_model(acs_itt_nona_dat, contr.treatment, save = FALSE)
```

```{r}
#| label: odds-ratio-summary-table-primary-model-save-trt-ctr
#| code-summary: Odds ratio summary table
#| tbl-cap: Posterior summaries for model parameters (fixed-effects).
odds_ratio_summary_table(res$drws$OR)
```

```{r}
#| code-summary: Odds ratio summary for epoch and site
#| fig-cap: Summary of epoch and site posterior odds ratios.
p <- plot_epoch_site_terms(
  exp(res$drws$gamma_epoch),
  exp(res$drws$gamma_site),
  factor(res$dat$region_by_site, 
         labels = c("India", "Australia\nNew Zealand", "Nepal"))
)
p
```

```{r}
#| fig-cap: Posterior densities for treatment comparisons.
p <- plot_or_densities(res$drws$compare)
p
```
