---
title: "8-0 Domain-specific secondary outcomes"
description: |
  This file runs through the descriptive summaries and analyses
  of the domain-specific secondary outcomes.
author:
  - name: James Totterdell
    affiliation: University of Sydney
  - name: Rob Mahar
    affiliation: University of Melbourne
date: last-modified
---

# Preamble

```{r}
#| label: pkgs
#| code-summary: Load packages
library(tidyverse)
library(labelled)
library(kableExtra)
library(cmdstanr)
library(posterior)
library(bayestestR)
library(bayesplot)
library(matrixStats)
library(plotly)
library(lubridate)
library(ggdist)
library(patchwork)

theme_set(theme_classic(base_size = 10, base_family = "Palatino") +
  theme(panel.grid = element_blank(),
        strip.background = element_blank()))
bayesplot_theme_set(theme_set(theme_classic(base_size = 10, base_family = "Palatino") +
  theme(panel.grid = element_blank(),
        strip.background = element_blank())))

color_scheme_set("red")
options(digits = 4)
```

```{r}
#| label: model
logistic_mod <- cmdstan_model("stan/logistic_bernoulli.stan")
primary_mod2 <- cmdstan_model("stan/primary_logistic_model_site_epoch2.stan")
primary_mod3 <- cmdstan_model("stan/primary_logistic_model_site_epoch3.stan")
```


```{r}
#| label: data
#| code-summary: Prepare dataset
devtools::load_all()
all_dat <- read_all_no_daily()
all_dat_daily <- read_all_daily()

acs_itt_dat <- all_dat %>% 
  filter_acs_itt() %>%
  mutate(
    # 8.0 death
    out_dth = D28_death,
    # 8.2 deep vein thrombosis
    out_dvt = case_when(
      D28_ABEventNone == "Yes" ~ 0,
      D28_ABEventUnknown == "Yes" ~ NA_real_,
      D28_ABDeepVein == "Yes" ~ 1,
      TRUE ~ 0
    ),
    # 8.3 - pulmonary embolism
    out_pe = case_when(
      D28_ABEventNone == "Yes" ~ 0,
      D28_ABEventUnknown == "Yes" ~ NA_real_,
      D28_ABPulmonaryEmbolism == "Yes" ~ 1,
      TRUE ~ 0
    ),
    # 8.4 - acute myocardial infarction
    out_ami = case_when(
      D28_ABEventNone == "Yes" ~ 0,
      D28_ABEventUnknown == "Yes" ~ NA_real_,
      D28_ABAcuteMyocardinalInfarction == "Yes" ~ 1,
      TRUE ~ 0
    ),
    # 8.5 - ischemic cerebrovascular event
    out_ice = case_when(
      D28_ABEventNone == "Yes" ~ 0,
      D28_ABEventUnknown == "Yes" ~ NA_real_,
      D28_ABIschemicCerebrovascularEvent == "Yes" ~ 1,
      TRUE ~ 0
    ),
    # 8.10 - other confirmed thrombotic event
    out_ote = case_when(
      D28_ABEventNone == "Yes" ~ 0,
      D28_ABEventUnknown == "Yes" ~ NA_real_,
      D28_ABOtherThromboEvent == "Yes" ~ 1,
      TRUE ~ 0
    ),
    # 8.1 - any thrombotic event or death
    out_ated = case_when(
      out_dth == 1 | out_dvt == 1 | out_pe == 1 | out_ami == 1  | out_ice == 1 | out_ote == 1 ~ 1,
      is.na(out_dth) | is.na(out_dvt) | is.na(out_pe) | is.na(out_ami) | is.na(out_ice) | is.na(out_ote) ~ NA_real_,
      out_dth == 0 & out_dvt == 0 & out_pe == 0 & out_ami == 0  & out_ice == 0 & out_ote == 0 ~ 0
    ),
    # 8.7 - major bleeding
    out_mb = case_when(
      D28_AECNone == "Yes" ~ 0,
      D28_AECMajorBleeding == "No" ~ 0,
      D28_AECMajorBleeding == "Yes" ~ 1,
      D28_AECUnknown == "Yes" ~ NA_real_,
      TRUE ~ 0 
    ),
    # 8.8 - non-major bleeding
    out_nmb = case_when(
      D28_ABNonMajorBleeding == "Yes" ~ 1,
      D28_ABNonMajorBleeding == "No" ~ 0,
      D28_ABNonMajorBleeding == "Unknown" ~ NA_real_
    ),
    # 8.6 - any clinically relevant bleeding
    out_crb = case_when(
      out_mb == 1 | out_nmb == 1 ~ 1,
      is.na(out_mb) | is.na(out_nmb) ~ NA_real_,
      out_mb == 0 & out_nmb == 0 ~ 0
    ),
    # 8.9 - heparain-induced thrombocytopenia
    out_hit = case_when(
      D28_AECNone == "Yes" ~ 0,
      D28_AECUnknown == "Yes" ~ NA_real_,
      D28_AECHIT == "Yes" ~ 1,
      TRUE ~ 0 
    )
  )
```

```{r}
#| label: cross-check-derived-variables
acs_itt_dat %>% dplyr::count(out_dvt, D28_ABDeepVein, D28_ABEventNone, D28_ABEventUnknown)
acs_itt_dat %>% dplyr::count(out_pe, D28_ABPulmonaryEmbolism, D28_ABEventNone, D28_ABEventUnknown)
acs_itt_dat %>% dplyr::count(out_ami, D28_ABAcuteMyocardinalInfarction, D28_ABEventNone, D28_ABEventUnknown)
acs_itt_dat %>% dplyr::count(out_ice, D28_ABIschemicCerebrovascularEvent, D28_ABEventNone, D28_ABEventUnknown)
acs_itt_dat %>% dplyr::count(out_ote, D28_ABOtherThromboEvent, D28_ABEventNone, D28_ABEventUnknown)
acs_itt_dat %>% dplyr::count(out_ated, out_dth, out_dvt, out_pe, out_ami, out_ice, out_ote)

acs_itt_dat %>% dplyr::count(D28_AECHIT, D28_AECMajorBleeding, D28_AECNone, D28_AECUnknown)
acs_itt_dat %>% dplyr::count(out_mb, D28_AECMajorBleeding, D28_AECNone, D28_AECUnknown)
acs_itt_dat %>% dplyr::count(out_nmb, D28_ABNonMajorBleeding)
acs_itt_dat %>% dplyr::count(out_crb, out_mb, out_nmb)

acs_itt_dat %>% dplyr::count(out_hit, D28_AECHIT, D28_AECNone, D28_AECUnknown)
```

# Descriptive

## Anticoagulation

The following table describes the anticoagulation domain-specific outcomes by anticoagulation intervention.

```{r}
gtab <- acs_itt_dat %>%
  select(CAssignment, out_dth, 
         out_ated, out_dvt, out_pe, out_ami, out_ice, out_ote, 
         out_crb, out_mb, out_nmb, out_hit) %>%
  group_by(CAssignment) %>%
  summarise(
    Randomised_ = n(),
    `Mortality_Died by day 28` = sprintf("%i (%.0f)", sum(out_dth, na.rm = TRUE), 100 * mean(out_dth, na.rm = TRUE)),
    `Mortality_Unknown` = sprintf("%i (%.0f)", sum(is.na(out_dth)), 100 * mean(is.na(out_dth))),
    `Thrombotic events_Unknown` = 
        sprintf("%i (%.0f)", sum(is.na(out_dvt)), 100 * mean(is.na(out_dvt))),
    `Thrombotic events_Deep vein thrombosis` = 
      sprintf("%i (%.0f)", sum(out_dvt, na.rm = TRUE), 100 * mean(out_dvt, na.rm = TRUE)),
    `Thrombotic events_Pulmonary embolus` = 
      sprintf("%i (%.0f)", sum(out_pe, na.rm = TRUE), 100 * mean(out_pe, na.rm = TRUE)),
    `Thrombotic events_Acute myocardial infarction` = 
      sprintf("%i (%.0f)", sum(out_ami, na.rm = TRUE), 100 * mean(out_ami, na.rm = TRUE)),
    `Thrombotic events_Ischemic cerebrovascular event` = 
      sprintf("%i (%.0f)", sum(out_ice, na.rm = TRUE), 100 * mean(out_ice, na.rm = TRUE)),
    `Thrombotic events_Other confirmed thrombotic event` = 
      sprintf("%i (%.0f)", sum(out_ote, na.rm = TRUE), 100 * mean(out_ote, na.rm = TRUE)),
    `Thrombotic events_Any thrombotic event or death` = 
      sprintf("%i (%.0f)", sum(out_ated, na.rm = TRUE), 100 * mean(out_ated, na.rm = TRUE)),
    `Bleeding_Unknown` = 
      sprintf("%i (%.0f)", sum(is.na(out_crb)), 100 * mean(is.na(out_crb))),
    `Bleeding_Major bleeding (as defined by ISTH)` = 
      sprintf("%i (%.0f)", sum(out_mb, na.rm = TRUE), 100 * mean(out_mb, na.rm = TRUE)),
    `Bleeding_Clinically relevant non-major bleeding` = 
      sprintf("%i (%.0f)", sum(out_nmb, na.rm = TRUE), 100 * mean(out_nmb, na.rm = TRUE)),
    `Bleeding_Any clinically relevant bleeding` = 
      sprintf("%i (%.0f)", sum(out_crb, na.rm = TRUE), 100 * mean(out_crb, na.rm = TRUE)),
    `Bleeding_Heparin-induced thrombocytopenia` = 
      sprintf("%i (%.0f)", sum(out_hit, na.rm = TRUE), 100 * mean(out_hit, na.rm = TRUE)),
  ) %>%
  gather(key, value, -CAssignment, factor_key = TRUE) %>%
  spread(CAssignment, value) %>%
  separate(key, c("Type", "Outcome"), sep = "_")
colnames(gtab)[-(1:2)] <- paste0(intervention_labels()$CAssignment[-1], "<br>(n = ", gtab[1, -(1:2)], ")")
gtab <- gtab[-1, ]

otab <- acs_itt_dat %>%
  select(CAssignment, out_dth, 
         out_ated, out_dvt, out_pe, out_ami, out_ice, out_ote, 
         out_crb, out_mb, out_nmb, out_hit) %>%
  group_by(CAssignment = "Overall") %>%
  summarise(
    Randomised_ = n(),
    `Mortality_Died by day 28` = sprintf("%i (%.0f)", sum(out_dth, na.rm = TRUE), 100 * mean(out_dth, na.rm = TRUE)),
    `Mortality_Unknown` = sprintf("%i (%.0f)", sum(is.na(out_dth)), 100 * mean(is.na(out_dth))),
    `Thrombotic events_Unknown` = 
        sprintf("%i (%.0f)", sum(is.na(out_dvt)), 100 * mean(is.na(out_dvt))),
    `Thrombotic events_Deep vein thrombosis` = 
      sprintf("%i (%.0f)", sum(out_dvt, na.rm = TRUE), 100 * mean(out_dvt, na.rm = TRUE)),
    `Thrombotic events_Pulmonary embolus` = 
      sprintf("%i (%.0f)", sum(out_pe, na.rm = TRUE), 100 * mean(out_pe, na.rm = TRUE)),
    `Thrombotic events_Acute myocardial infarction` = 
      sprintf("%i (%.0f)", sum(out_ami, na.rm = TRUE), 100 * mean(out_ami, na.rm = TRUE)),
    `Thrombotic events_Ischemic cerebrovascular event` = 
      sprintf("%i (%.0f)", sum(out_ice, na.rm = TRUE), 100 * mean(out_ice, na.rm = TRUE)),
    `Thrombotic events_Other confirmed thrombotic event` = 
      sprintf("%i (%.0f)", sum(out_ote, na.rm = TRUE), 100 * mean(out_ote, na.rm = TRUE)),
    `Thrombotic events_Any thrombotic event or death` = 
      sprintf("%i (%.0f)", sum(out_ated, na.rm = TRUE), 100 * mean(out_ated, na.rm = TRUE)),
    `Bleeding_Unknown` = 
      sprintf("%i (%.0f)", sum(is.na(out_crb)), 100 * mean(is.na(out_crb))),
    `Bleeding_Major bleeding (as defined by ISTH)` = 
      sprintf("%i (%.0f)", sum(out_mb, na.rm = TRUE), 100 * mean(out_mb, na.rm = TRUE)),
    `Bleeding_Clinically relevant non-major bleeding` = 
      sprintf("%i (%.0f)", sum(out_nmb, na.rm = TRUE), 100 * mean(out_nmb, na.rm = TRUE)),
    `Bleeding_Any clinically relevant bleeding` = 
      sprintf("%i (%.0f)", sum(out_crb, na.rm = TRUE), 100 * mean(out_crb, na.rm = TRUE)),
    `Bleeding_Heparin-induced thrombocytopenia` = 
      sprintf("%i (%.0f)", sum(out_hit, na.rm = TRUE), 100 * mean(out_hit, na.rm = TRUE)),
  ) %>%
  gather(key, value, -CAssignment, factor_key = TRUE) %>%
  spread(CAssignment, value) %>%
  separate(key, c("Type", "Outcome"), sep = "_")
colnames(otab)[-(1:2)] <- paste0("Overall<br>(n = ", otab[1, -(1:2)], ")")
otab <- otab[-1, ]

tab <- left_join(gtab, otab, by = c("Type", "Outcome"))

kable(
  tab[, -1],
  booktabs = TRUE,
  align = "lrrrr",
  escape = T
) %>%
  kable_styling(
    latex_options = "HOLD_position"
  ) %>%
  pack_rows("Mortality", 1, 2) %>%
  pack_rows("Thrombotic events", 3, 9) %>%
  pack_rows("Bleeding", 10, 14)
```

```{r}
colnames(tab) <- linebreak(colnames(tab), align = "c", linebreaker = "<br>")
out <- kable(
  tab[, -1],
  format = "latex",
  booktabs = TRUE,
  align = "lrrrrr",
  escape = FALSE
) %>%
  kable_styling(
    font_size = 9,
    latex_options = "HOLD_position"
  ) %>%
  pack_rows("Mortality", 1, 2) %>%
  pack_rows("Thrombotic events", 3, 9) %>%
  pack_rows("Bleeding", 10, 14)
save_tex_table(out, file.path("outcomes", "secondary", "8-0-anticoagulation-specific-summary"))
```


# Modelling

The SAP only requests formal analyses of the two composite outcomes:

- any thrombotic event or death
- any clinically relevant bleeding

Due to small numbers (6 events from 1,521 cases ~ 0.4%), the analysis of "any clinically relevant bleeding" has not been undertaken.

The analysis of any thrombotic event or death will largely be driven by death due to the small number of thrombotic events. Therefore, the result is likely to be similar to that obtained for all-cause mortality. In any event, this analysis is undertaken below.

## Primary Model

```{r}
acs_itt_nona_dat <- acs_itt_dat %>%
  filter(!is.na(out_ated)) %>%
  transmute_model_cols_grp_aus_nz() %>%
  left_join(acs_itt_dat %>% 
              select(StudyPatientID, out_ated), 
            by = "StudyPatientID")

ctr <- contr.orthonorm
X <- model.matrix(
  ~ CAssignment + AAssignment + agegte60 + inelgc3 + ctry,
  data = acs_itt_nona_dat,
  contrasts.arg = list(CAssignment = ctr, AAssignment = ctr)
)
nXassign <- sum(grepl("Assignment", colnames(X)))
epoch  <- acs_itt_nona_dat$epoch
M_epoch  <- max(acs_itt_nona_dat$epoch)
region <- acs_itt_nona_dat[["ctry_num"]]
M_region <- max(region)
site <- acs_itt_nona_dat[["site_num"]]
M_site <- max(site)
region_by_site <- region_by_site <- acs_itt_nona_dat %>% 
  dplyr::count(ctry_num, site_num) %>% 
  pull(ctry_num)
epoch_map <- acs_itt_nona_dat %>% dplyr::count(epoch, epoch_lab)
site_map <- acs_itt_nona_dat %>% dplyr::count(site_num, site)

mdat <- list(N = nrow(X), K = ncol(X), X = X, y = acs_itt_nona_dat$out_ated,
       M_region = M_region, M_site = M_site, site = site,
       M_epoch = M_epoch, epoch = epoch,
       region_by_site = region_by_site,
       beta_mu = c(0, rep(0, 9)),
       beta_sd = c(2.5, rep(1, nXassign), 2.5, 10, rep(1, 2)))

snk <- capture.output(
  mfit <- primary_mod3$sample(
    data = mdat,
    seed = 28497,
    refresh = 0,
    iter_warmup = 1000,
    iter_sampling = 2500,
    chains = 8,
    parallel_chains = 8,
    adapt_delta = 0.98
))
drws <- as_draws_rvars(mfit$draws(c("beta", "gamma_epoch", "gamma_site", "tau_epoch", "tau_site")))

names(drws$beta) <- colnames(X)
names(drws$gamma_epoch) <- epoch_map$epoch_lab
names(drws$gamma_site) <- site_map$site

drws$treat <- (transform_coding(cbind(1, contr.orthonorm(4)), cbind(1, contr.treatment(4))) %**%
  drws$beta[1:4])[2:4]

drws$OR <- exp(c(rvar(0), drws$treat, rvar(0), drws$beta[7], rvar(0), drws$beta[8], rvar(0), drws$beta[9:10]))
names(drws$OR) <- c(
  "Standard (ref)", "Intermediate", "Standard plus aspirin", "Therapeutic", 
  "Age < 60 (ref)", "Age 60+", "Eligible aspirin (ref)", "Ineligible aspirin", 
  "India (ref)", "Australia/NZ", "Nepal")
```

```{r}
odds_ratio_summary_table(drws$OR)
```

```{r}
#| label: odds-ratio-summary-table-primary-model-save
save_tex_table(
  odds_ratio_summary_table(drws$OR, "latex"),
  "outcomes/secondary/8-1-primary-model-acs-itt-summary-table")
```


```{r}
epoch_rvs <- exp(drws$gamma_epoch)
site_rvs <- exp(drws$gamma_site)

orsdat <- tibble(
  Group = "Epoch",
  Parameter = fct_inorder(names(epoch_rvs)),
  posterior = epoch_rvs
)
p_epoch <- ggplot(orsdat, aes(xdist = posterior, y = Parameter)) +
  stat_pointinterval(.width = c(0.75, 0.95), fatten_point = 1.5) +
  geom_vline(xintercept = 1, linetype = 2) +
  scale_x_log10("Odds ratio (log scale)") +
  labs(y = "Epoch")

orsdat <- tibble(
  Group = "Site",
  Region = factor(mdat$region_by_site, labels = c("India", "Australia/NZ", "Nepal")),
  Parameter = fct_inorder(names(site_rvs)),
  posterior = site_rvs
)
p_site <- ggplot(orsdat, aes(xdist = posterior, y = Parameter)) +
  facet_grid(Region ~ ., scales = "free_y", space = "free_y") +
  stat_pointinterval(.width = c(0.75, 0.95), fatten_point = 1.5) +
  geom_vline(xintercept = 1, linetype = 2) +
  scale_x_log10("Odds ratio (log scale)") +
  labs(y = "Site") +
  theme(panel.border = element_rect(fill = NA))

p <- p_epoch | p_site
p
```

```{r}
pth <- file.path("outputs", "figures", "outcomes", "secondary", "8-1-primary-model-epoch-site-terms.pdf")
ggsave(pth, p, width = 6, height = 4.5)
```

### Prior Sensitivity

The analysis is repeated using treatment coding rather than the orthonormal coding. Due to the change in prior, the is a slight shift in the estimated treatment effects, however this does not alter the result of weak evidence for any difference.

```{r}
ctr <- contr.treatment
X <- model.matrix(
  ~ CAssignment + AAssignment + agegte60 + inelgc3 + ctry,
  data = acs_itt_nona_dat,
  contrasts.arg = list(CAssignment = ctr, AAssignment = ctr)
)
nXassign <- sum(grepl("Assignment", colnames(X)))
epoch  <- acs_itt_nona_dat$epoch
M_epoch  <- max(acs_itt_nona_dat$epoch)
region <- acs_itt_nona_dat[["ctry_num"]]
M_region <- max(region)
site <- acs_itt_nona_dat[["site_num"]]
M_site <- max(site)
region_by_site <- region_by_site <- acs_itt_nona_dat %>% 
  dplyr::count(ctry_num, site_num) %>% 
  pull(ctry_num)
epoch_map <- acs_itt_nona_dat %>% dplyr::count(epoch, epoch_lab)
site_map <- acs_itt_nona_dat %>% dplyr::count(site_num, site)

mdat <- list(N = nrow(X), K = ncol(X), X = X, y = acs_itt_nona_dat$out_ated,
       M_region = M_region, M_site = M_site, site = site,
       M_epoch = M_epoch, epoch = epoch,
       region_by_site = region_by_site,
       beta_mu = c(0, rep(0, 9)),
       beta_sd = c(2.5, rep(1, nXassign), 2.5, 10, rep(1, 2)))

snk <- capture.output(
  mfit <- primary_mod3$sample(
    data = mdat,
    seed = 28497,
    refresh = 0,
    iter_warmup = 1000,
    iter_sampling = 2500,
    chains = 8,
    parallel_chains = 8,
    adapt_delta = 0.98
))
drws <- as_draws_rvars(mfit$draws(c("beta", "gamma_epoch", "gamma_site", "tau_epoch", "tau_site")))

names(drws$beta) <- colnames(X)
names(drws$gamma_epoch) <- epoch_map$epoch_lab
names(drws$gamma_site) <- site_map$site

drws$OR <- exp(c(rvar(0), drws$beta[2:4], rvar(0), drws$beta[7], rvar(0), drws$beta[8], rvar(0), drws$beta[9:10]))
names(drws$OR) <- c(
  "Standard (ref)", "Intermediate", "Standard plus aspirin", "Therapeutic", 
  "Age < 60 (ref)", "Age 60+", "Eligible aspirin (ref)", "Ineligible aspirin", 
  "India (ref)", "Australia/NZ", "Nepal")
```

```{r}
odds_ratio_summary_table(drws$OR)
```

```{r}
epoch_rvs <- exp(drws$gamma_epoch)
site_rvs <- exp(drws$gamma_site)

orsdat <- tibble(
  Group = "Epoch",
  Parameter = fct_inorder(names(epoch_rvs)),
  posterior = epoch_rvs
)
p_epoch <- ggplot(orsdat, aes(xdist = posterior, y = Parameter)) +
  stat_pointinterval(.width = c(0.75, 0.95), fatten_point = 1.5) +
  geom_vline(xintercept = 1, linetype = 2) +
  scale_x_log10("Odds ratio (log scale)") +
  labs(y = "Epoch")

orsdat <- tibble(
  Group = "Site",
  Region = factor(mdat$region_by_site, labels = c("India", "Australia/NZ", "Nepal")),
  Parameter = fct_inorder(names(site_rvs)),
  posterior = site_rvs
)
p_site <- ggplot(orsdat, aes(xdist = posterior, y = Parameter)) +
  facet_grid(Region ~ ., scales = "free_y", space = "free_y") +
  stat_pointinterval(.width = c(0.75, 0.95), fatten_point = 1.5) +
  geom_vline(xintercept = 1, linetype = 2) +
  scale_x_log10("Odds ratio (log scale)") +
  labs(y = "Site") +
  theme(panel.border = element_rect(fill = NA))

p <- p_epoch | p_site
p
```
